\separator
\subsection{Research projects}

\subsubsection{Faculty Start-Up Grants}

\begin{description}

  \item[February 2023 -- January 2025] Project title: ``\textit{Nonlinear waves in geophysics and biomechanics}'', project number: FSU-2023-014. Funded by the Khalifa University of Science and Technology. Total cost: \textbf{1\,426\,232.49 AED}

\end{description}

\separator
\subsubsection{ANR projects}

ANR = \href{http://www.agence-nationale-recherche.fr/}{Agence Nationale de la Recherche}

\begin{itemize}

  \item[$\blacktriangleright$] L'\'Ecole Universitaire de Recherche (EUR) ``\textbf{Solar Academy}'' created at the University Savoie Mont Blanc in the framework of the ``Programme d'Investissement d'Avenir'' (PIA3). Project leader: Prof. Monika \textsc{Woloszyn} (LOCIE/USMB)

  \item[$\blacktriangleright$] Project \textbf{FRAISE} (2016 -- 2020): ``\textit{Absorbent falling film with free-surface instabilities: exploration}''. Principal investigator: C.~\textsc{Ruyer}-\textsc{Quil} (LOCIE, Polytech Annecy--hamb\'ery and Universit\'e Savoie Mont Blanc, Chamb\'ery, France)

  \item[$\blacktriangleright$] Project \textbf{MathOc\'ean} (2009 -- 2012): ``\textit{Analyse math\'ematique en oc\'eanographie et applications}''. Principal investigator: D.~\textsc{Lannes} (DMA, ENS Paris, France)
  
  \item[$\blacktriangleright$] Project \textbf{HEXECO} (2007 -- 2010): ``\textit{Hydrodynamique extr\^eme du large \`a la c\^ote}''. Principal investigator: O.~\textsc{Kimmoun} (Ecole Centrale Marseille, France)
  
\end{itemize}

\separator
\subsubsection{International cooperation projects}

\begin{itemize}

  \item[$\blacktriangleright$] \textbf{AAP USMB} (2020) of the University Savoie Mont Blanc: ``\textit{Genesis and propagation of a tsunami wave on an accretionary prism}''. Co-PI: Prof. Emeritus Christian~\textsc{Beck} (ISTerre, USMB). Cooperation with Prof. Valery \textsc{Liapidevskii} from the Lavrentyev Institute of Hydrodynamics, SB RAS, Novosibirsk, Russia.

  \item[$\blacktriangleright$] \textbf{AAP USMB} (2018) of the University Savoie Mont Blanc: ``\textit{Nonlinear waves on adaptive moving meshes}''. Cooperation with the Victoria University of Wellington (New Zealand) and the University of Valladolid (Spain)

  \item[$\blacktriangleright$] \textbf{Partnership Hubert Curien (PHC) -- Parrot 2017} (French -- Estonian cooperation). Project title: ``The effect of beach roughness on sea wave run-up''. Partner: Tallinn University of Technology and Marine Systems Institute, Tallinn, Estonia. French PI: D.~\textsc{Dutykh} (LAMA, University Savoie Mont Blanc), Estonian PI: I.~\textsc{Didenkulova} (Marine Systems Institute, TalTech, Estonia)

  \item[$\blacktriangleright$] \textbf{LEA Math Mode} (Laboratoire Europ\'een Associ\'e CNRS Franco--Roumain Math\'e\-matiques et Mod\'elisation) (2015 -- 2016) project ``\textit{A variational approach to water waves in shallow waters}''. Cooperation with Dr.~Delia~\textsc{Ionescu-Kruse} (IMAR, Bucharest, Romania)
  
  \item[$\blacktriangleright$] \textbf{AAP Montagne} (2016) of the University Savoie Mont Blanc: ``\textit{Modelling and simulation of sliding masses}''. Cooperation with Prof. Valery \textsc{Liapidevskii} from the Lavrentyev Institute of Hydrodynamics, SB RAS, Novosibirsk, Russia
  \item[$\blacktriangleright$] French--Russian cooperative project (\textbf{Convention d'\'echange}) \No EDC26179 (2014 -- 2015) ``\textit{Interaction of waves with obstacles}''. Cooperation with Prof. G.~\textsc{Khakimzyanov} (Institute of Computational Technologies, SB RAS, Novosibirsk, Russia)
	\item[$\blacktriangleright$] Project \textbf{PICS CNRS} (2010 -- 2012) ``\textit{Numerical simulation of higly nonlinear water waves}''. Cooperation with the Institute of Computational Technologies, Siberian Branch of Russian Academy of Sciences and Novosibirsk State University. French leader: D.~\textsc{Dutykh} (LAMA, University of Savoie), Russian leader: Yu.~\textsc{Shokin} (academician, director of Institute of Computational Technologies)
	\item[$\blacktriangleright$] \textbf{Partnership Hubert Curien (PHC) -- ULYSSES 2010} (French -- Irish cooperation). Project title: ``\textit{Numerical Models for Compressible and Incompressible Flows and Applications}''. Partners: School of Mathematical Sciences (University College Dublin), CMLA (ENS de Cachan) and LAMA, University of Savoie. French leader: D.~\textsc{Dutykh} (LAMA, University of Savoie), Irish leader: T.~\textsc{Cox} (School of Mathematical Sciences, University College Dublin)
  \item[$\blacktriangleright$] \textbf{CNRS/Russian Academy of Sciences exchange program} (2009 -- 2011). Project title ``\textit{Analytical and numerical solutions for the models of powder-snow avalanches}''. French leader: D.~\textsc{Dutykh} (LAMA, University of Savoie), Russian partner leader: V.~\textsc{Liapidevskii} (Lavrentyev Institute of Hydrodynamics, Novosibirsk)
\end{itemize}

\separator
\subsubsection{Other projects}
\begin{itemize}
    \item[$\blacktriangleright$] Project \textbf{PEPS CNRS \'Energie} (2017) ``\textit{Innovative numerical methods for more energetically efficient buildings}''. Partners: LOCIE UMR 5271 (Polytech Annecy--Chamb\'ery). Project leader: D.~\textsc{Dutykh} (LAMA, University Savoie Mont Blanc)
    \item[$\blacktriangleright$] Project \textbf{PEPS CNRS InPhyNiTi} (INSMI/INP) (2014 -- 2015) ``\textit{Faraday instability in  the Hele-Shaw cell}''. Partners: Laboratory J.-A.~Dieudonn\'e (LJAD, University of Nice Sophia Antipolis), Laboratory of the Condensed Matter Physics (LPMC, University of Nice Sophia Antipolis), Laboratory of Mathematics (LAMA, University Savoie Mont Blanc). Project leader: D.~\textsc{Dutykh} (LAMA, University Savoie Mont Blanc)
    \item[$\blacktriangleright$] Project \textbf{PEPS CNRS} (INP) (2010 -- 2011) ``\textit{Numerical simulation of nonlinear waves in variable medium}''. Partners: Laboratory J.-A.~Dieudonn\'e (LJAD, University of Nice Sophia Antipolis), Laboratory of the Condensed Matter Physics (LPMC, University of Nice Sophia Antipolis), Laboratory of Mathematics (LAMA, University of Savoie). Project leader: D.~\textsc{Dutykh} (LAMA, University of Savoie)
    \item[$\blacktriangleright$] Contract with r\'egion Rh\^one-Alpes (Cluster Environnement): ``\textit{Numerical simulation of snow avalanches}'' (2009 -- 2010)
    \item[$\blacktriangleright$] Project \textbf{PEPS CNRS} (INS2I) (2009 -- 2010) ``\textit{PML, l'arithm\'etique et le calcul: vers l'arithm\'etique et le calcul num\'erique efficace et \'el\'egamment certifi\'e}''. Partners: teams LIMD and EDPs\up{2} of LAMA, University of Savoie. Project leader: C.~\textsc{Raffalli} (LAMA, University of Savoie)
\end{itemize}