\separator
\subsection{Publications}

\begin{itemize}
  \item[$\blacktriangleright$] My \textsc{Erd\H{o}s} number: \textbf{3}
  \item[$\blacktriangleright$] My $h-$index\footnote{This information is retrieved from Google Scholar server.}: \textbf{41}
  \item[$\blacktriangleright$] My ORCID number: $0000-0001-5247-2788$
  \item[$\blacktriangleright$] Citations statistics: \url{https://scholar.google.com/citations?user=cvOVca4AAAAJ}
\end{itemize}

\separator
\subsubsection{Preprints under review}

\begin{etaremune}

  \item D.~Batic, \textbf{D.~Dutykh} and M.~Sukaiti. \textit{Exact Spinning Morris--Thorne Wormhole: Causal Structure, Shadows, and Multipole Moments}. Submitted, 2026 % No - (Arxiv, HAL, RG)

  \item D.~Batic, \textbf{D.~Dutykh} and M.~Sukaiti. \textit{Exact Spinning Morris--Thorne Wormhole with Ergoregion and Stable Causality}. Submitted, 2026 % No - (Arxiv, HAL, RG)

  \item P.~Kundu, S.~Sarkar and \textbf{D.~Dutykh}. \textit{Viscoelastic Deformation Analysis of a Non-Planar Fault in Burger's Rheology Medium}, Submitted, 2026 % No (HAL & Arxiv)

  \item D.~Batic, \textbf{D.~Dutykh} and M.~Sukaiti. \textit{Exact solutions for slowly rotating wormholes in the presence of an anisotropic fluid}. Submitted, 2025 % No - (Arxiv, HAL, RG)

  \item M.~Zafar, P.~Sabatier, \textbf{D.~Dutykh}, W.~Rapuc, R.~Paris, A.~Piccin, P.~Vuillemin and F.~Anselmetti. \textit{Human-Enhanced Tsunami Hazard in Large Lakes}. Submitted, 2025 % No - (Arxiv, HAL, RG)

  \item D.~Batic, \textbf{D.~Dutykh} and F.~Scardigli. \textit{Spectral Analysis of Quasinormal Modes of Planck Stars}. Submitted, 2025 % No - (Arxiv, HAL, RG)

  \item A.~Rashidi, \textbf{D.~Dutykh} and M.~Mokhtari. \textit{Primarily tsunami modeling of the Mw 8.8 Kamchatka Peninsula earthquake on July 29, 2025}. Submitted, 2025 % No - (Arxiv, HAL, RG)

  \item D.~Batic, \textbf{D.~Dutykh} and M.~Sukaiti. \textit{Noncommutative geometry-inspired wormholes supported by quasi-de Sitter and Chaplygin-like equations of state}. Submitted, 2025 % No - (Arxiv, HAL, RG)

  \item D.~Batic and \textbf{D.~Dutykh}. \textit{Gauss--Bonnet fingerprints in black-hole ringdowns}. Submitted, 2025 % No - (Arxiv, HAL, RG)

  \item D.~Batic and \textbf{D.~Dutykh}. \textit{Scalar Quasinormal Modes of Gauss--Bonnet Black Holes via the Spectral Method}. Submitted, 2025 % No - (Arxiv, HAL, RG)

  \item D.~Batic and \textbf{D.~Dutykh}. \textit{Vector Quasinormal Modes of Gauss--Bonnet Black Holes via the Spectral Method}. Submitted, 2025 % No - (Arxiv, HAL, RG)
  
  \item D.~Batic and \textbf{D.~Dutykh}. \textit{Tensor Quasinormal Modes of Gauss--Bonnet Black Holes via the Spectral Method}. Submitted, 2025 % No - (Arxiv, HAL, RG)

  \item R.~Escobedo, \textbf{D.~Dutykh}, and L.~Spector. \textit{Group size effect on the success of wolves hunting}. Submitted, 2025 \\ % Arxiv
  \url{https://hal.archives-ouvertes.fr/hal-01182799/}

  \item A.~Deeb, \textbf{D.~Dutykh} and M.~Al~Zohbi. \textit{Error estimation for numerical approximations of ODEs via composition techniques. Part II: Backward difference formulas}. Submitted, 2023 % No (HAL, Arxiv, RG)

  \item A.~Deeb and \textbf{D.~Dutykh}. \textit{Error estimation for numerical approximations of ODEs via composition techniques. Part I: One-step methods}. Submitted, 2023 % Yes - (Arxiv), No - (HAL, RG)

\end{etaremune}

\separator
\subsubsection{Books}

\begin{etaremune}

  \item D.~Clamond, \textbf{D.~Dutykh} and D.~Mitsotakis. \textit{Variational approach to water wave modelling}, IAHR WATER MONOGRAPHS, International Association for Hydro-Environment Engineering and Research (IAHR), Spain, 2024. ISBN: $978-90-833476-6-0$ \\
  \url{https://www.iahr.org/library/infor?pid=29802/}

  \item S.~Lespinats, B.~Colange and \textbf{D.~Dutykh}. \textit{Nonlinear Dimensionality Reduction Techniques: A Data Structure Preservation Approach}, Springer, 2022. ISBN: $978-3-030-81025-2$ \\
  \url{https://www.springer.com/gp/book/9783030810252/}

  \item G.~Khakimzyanov, \textbf{D.~Dutykh}, Z.~Fedotova and O.~Gusev. \textit{Dispersive Shallow Water Waves: Theory, Modeling, and Numerical Methods}, 1\up{st} Ed., Birkh\"auser Basel, Springer Nature Switzerland AG, 263 pp., 2020. ISBN: $978-3-030-46266-6$ \\
  \url{https://www.springer.com/gp/book/9783030462666/}

  \item N.~Mendes, M.~Chhay, J.~Berger and \textbf{D.~Dutykh}. \textit{Numerical methods for diffusion phenomena in building physics: a practical introduction}, 2\up{nd} Ed., Springer, Cham, Switzerland, 251 pp., 2020. ISBN: $978-3-030-31573-3$ \\
  \url{https://www.springer.com/gp/book/9783030315733/}

  \item N.~Mendes, M.~Chhay, J.~Berger and \textbf{D.~Dutykh}. \textit{Numerical methods for diffusion phenomena in building physics}, PUCPRESS, Curitiba, Brazil, 224 pp., 2017. ISBN: $978-8-568-32488-2$ \\
  \url{https://books.google.com/books?id=KNcuDwAAQBAJ}
  
\end{etaremune}

\separator
\subsubsection{International peer-reviewed journals}

\listpartsep = 1ex

\begin{etaremune}

  %%% 2026: (2)

  \listpart{\centering\large\textbf{-- 2026 --}}

  \item M.~Hunt and \textbf{D.~Dutykh}. \textit{Free Surface Waves in Electrohydrodynamics with Prescribed Vorticity Distribution}. Accepted to Math. Methods Appl. Sci., 2025 % No (HAL & Arxiv)

  \item S.~Mukherjee, L.~Vuillon, \textbf{D.~Dutykh} and I.~Tsanakas. \textit{Scalable weather data reduction for solar PV analysis using graph-based approach}. Accepted to Energy Systems, 2025 % Yes - HAL, No - (Arxiv, RG)
  \url{https://hal.science/hal-05235714/}

  %%% 2025: (10)
  
  \listpart{\centering\large\textbf{-- 2025 --}}
  
  \item M.~Zafar, \textbf{D.~Dutykh}, R.~Paris, R.~Gastineau, J.~De Sigoyer, E.~Duarte, N.~\"Unsal, N.~Harrichhausen, S.~Flavard, M.~\c{S}ahin and P.~Sabatier. \textit{Strike-Slip Fault-Generated Paleotsunamis in Lake Iznik (NW T\"{u}rkiye): Numerical Modeling Corroborated by Coastal Deposits}. Geophys. Res. Lett., \textbf{52}(18), e2025GL117422, 2025 \\ % Yes - (HAL & RG), No - Arxiv
  \url{https://hal.science/hal-05293993/}

  \item D.~Batic, \textbf{D.~Dutykh}, and Z.~Babou. \textit{Quasinormal modes of noncommutative geometry-inspired dirty black holes}. Proc. R. Soc. A, \textbf{481}(2318), 20250021, 2025 \\ % No (HAL, Arxiv, RG)
  \url{https://arxiv.org/abs/2507.19107/}

  \item S.~Savvopoulos, A.~Al-Aghbari, K.~El Kadi, \textbf{D.~Dutykh} and I.~Janajreh. \textit{Advancing Freeze Desalination through Ultrasound-Enhanced Modelling: Case Studies and Insights for Commercial Applications}. Case Stud. Therm. Eng., \textbf{73}, 106518, 2025 % No (HAL & Arxiv, RG)

  \item M.~Zafar, P.~Sabatier, \textbf{D.~Dutykh}, H.~Jomard, W.~Rapuc, P.~Lajeunesse and E.~Chapron. \textit{Modelling earthquake-induced seiche process and subsequent homogenite deposits in lacustrine setting}. Earth Planet. Sci. Lett., \textbf{660}, 119348, 2025 % Yes - RG, No - (HAL, Arxiv)

  \item D.~Batic, \textbf{D.~Dutykh} and J.~Beek. \textit{A Spectral Approach for Quasinormal Frequencies of Noncommutative Geometry-inspired Wormholes}. Class. Quantum Gravity, \textbf{42}(8), 085003, 2025 \\ % Yes - (Arxiv & RG), No - HAL
  \url{https://arxiv.org/abs/2504.02370/}

  \item M.~Amazioug, J.-X. Peng, \textbf{D.~Dutykh} and M.~Asjad. \textit{Emergence and enhancement of feedback control induced quantum entanglement}. Eur. Phys. J. Plus, \textbf{140}, 132, 2025 \\ % Yes (Arxiv), No (HAL, RG)
  \url{https://arxiv.org/abs/2311.06578/}

  \item A.~Deeb and \textbf{D.~Dutykh}. \textit{Numerical integration of Navier--Stokes equations by time series expansion and stabilized FEM}, Math. Comput. Simul., \textbf{233}, 208--236, 2025 \\ % Yes - HAL & RG, No - Arxiv
  \url{https://hal.science/hal-04932473/}

  \item D.~Batic and \textbf{D.~Dutykh}. \textit{Instability Analysis of Massive Static Phantom Wormholes via the Spectral Method}. Eur. Phys. J. C, \textbf{85}, 144, 2025 \\ % Yes - Arxiv, RG, No - HAL
  \url{https://arxiv.org/abs/2502.05486/}

  \item \textbf{D.~Dutykh} and E.~Leichtnam. \textit{On complex algebraic singularities of some genuinely nonlinear PDEs}. Rend. Mat. Appl. (7), \textbf{46}(1-2), 63--150, 2025 \\ % Yes - HAL & Arxiv, No - RG
  \url{https://hal.science/hal-03372673/}

  \item \textbf{D.~Dutykh} and Ya.~Prykarpatsky. \textit{On integrability of a new dynamical system associated with the BBM-type hydrodynamic flow}, Math. Methods Appl. Sci., \textbf{48}(1), 107--121, 2025 \\ % Yes - Ariv & RG, No - HAL
  \url{https://arxiv.org/abs/2407.07900/}

  %%% 2024: (12)

  \listpart{\centering\large\textbf{-- 2024 --}}

  \item A.~Rashidi, M.~Mokhtari, \textbf{D.~Dutykh}, M.~Masoodi, P.~Faridi and S.~Kiani. \textit{Researching Tsunami Hazards in Makran: Insights into Challenges and Complex Tsunamis}. J. Seismol. Earthq. Eng., \textbf{26}(4), 71--85, 2024 % Yes - RG,  No - (HAL, Arxiv)

  \item D.~Batic, \textbf{D.~Dutykh} and B.L.~Giacchini. \textit{A unified spectral approach for quasinormal modes of Lee--Wick black holes}, Phys. Rev. D, \textbf{110}, 084032, 2024 \\ % No (HAL, Arxiv, RG)
  \url{https://arxiv.org/abs/2410.13245/}

  \item D.~Batic and \textbf{D.~Dutykh}. \textit{A Unified Spectral Approach for Quasinormal Modes of Morris--Thorne Wormholes}. Class. Quantum Gravity, \textbf{41}(21), 215003, 2024 \\ % Yes - RG & Arxiv, No (HAL)
  \url{https://arxiv.org/abs/2410.05979/}

  \item P.~Djorw\'e, M.~Asjad, Y.~Pennec, \textbf{D.~Dutykh} and B.~Djafari-Rouhani. \textit{Parametrically enhancing sensor sensitivity at an exceptional point}. Phys. Rev. Res., \textbf{6}, 033284, 2024 \\ % Yes - (Arxiv, HAL & RGF)
  \url{https://arxiv.org/abs/2312.05057/}
  
  \item F.~Carbone and \textbf{D.~Dutykh}. \textit{Route to chaos and resonant triads interaction in a truncated Rotating Nonlinear shallow-water model}, PLoS One, \textbf{19}(8), e0305534, 2024 \\ % Yes - (HAL, Arxiv & RG)
  \url{https://hal.science/hal-04670019/}

  \item C.~Edet, M.~Asjad, \textbf{D.~Dutykh}, N.~Ali and O.~Abah. \textit{Entropy production rate and correlations of cavity magnomechanical system}. Phys. Rev. Res., \textbf{6}, 033037, 2024 \\ % Yes - Arxiv & RG, No - HAL
  \url{https://arxiv.org/abs/2401.16857/}

  \item A.~Deeb and \textbf{D.~Dutykh}. \textit{Stabilized Time Series Expansions for High-Order Finite Element Solutions of Partial Differential Equations}. Stud. Appl. Math., \textbf{153}(2), e12708, 2024 \\ % Yes (HAL, Arxiv, RG)
  \url{https://hal.science/hal-04582473/}
  
  \item C.~C\'ardenas-Bravo, \textbf{D.~Dutykh} and S.~Lespinats. \textit{On the parameters domain of the single-diode model}, Solar Energy, \textbf{277}, 112718, 2024 \\ % Yes - (Arxiv, HAL & RG)
  \url{https://hal.science/hal-04622649/}
  
  \item D.~Batic and \textbf{D.~Dutykh}. \textit{Quasinormal Modes in Noncommutative Schwarzschild Black Holes: A Spectral Analysis}. Eur. Phys. J. C, \textbf{84}, 622, 2024 \\ % Yes - (Arxiv), No - (HAL, RG)
  \url{https://arxiv.org/abs/2406.03353/}

  \item M.~Zafar, \textbf{D.~Dutykh}, P.~Sabatier, M.~Banjan and J.~Kim. \textit{Simulating Sublacustrine Landslide-Induced Paleotsunami in NW Alpine Lake at the Younger Dryas --- Early Holocene climatic transition}. J. Geophys. Res. Solid Earth, \textbf{129}(5), e2023JB028629, 2024 \\ % Yes (Arxiv & RG), No - (Arxiv) 
  \url{https://hal.science/hal-04592536/}
  
  \item M.~Amazioug, \textbf{D.~Dutykh}, B.~Teklu and M.~Asjad. \textit{Achieving Strong Magnon Blockade through Magnon Squeezing in a Cavity Magnetomechanical System}, Annalen der Physik, \textbf{536}(4), 2300357, 2024 \\ % Yes (Arxiv & RG), No (HAL)
  \url{https://arxiv.org/abs/2308.06367/}
  
  \item M.~Bowen, P.~Samozino, M.~Vonderscher, \textbf{D.~Dutykh} and B.~Morel. \textit{Mathematical modeling of exercise fatigability in the severe domain: A unifying integrative framework in isokinetic condition}, Journal of Theoretical Biology, \textbf{578}, 111696, 2024 \\ % Yes (HAL), No (Arxiv, RG)
  \url{https://hal.science/hal-04330250/}
  % 10.1016/j.jtbi.2023.111696
  
  %%% 2023: (6)
  
  \listpart{\centering\large\textbf{-- 2023 --}}

  \item A.~Rashidi, \textbf{D.~Dutykh} and Ch.~Beck. \textit{Correction to: Modeling the potential genesis of tsunamis from below an accretionary prism and their potential impact: a case study along the eastern boundary of the Caribbean Plate}, Natural Hazards, \textbf{118}, 1765, 2023 % No (HAL & Arxiv)
  % 10.1007/s11069-023-06071-1
  
  \item A.~Rashidi, \textbf{D.~Dutykh} and Ch.~Beck. \textit{Modeling the potential genesis of tsunamis from below an accretionary prism, and their potential impact: a case study along the eastern boundary of the Caribbean Plate}, Natural Hazards, \textbf{118}, 307--329, 2023 % No (HAL & Arxiv)
  % 10.1007/s11069-023-06004-y

  \item A.~Cheviakov and \textbf{D.~Dutykh}. \textit{Galilei-invariant and energy-preserving extensions of the Benjamin--Bona--Mahony-type equations}, Partial Differ. Equations Appl. Math., \textbf{7}, 100519, 2023 % No (HAL & Arxiv)
  % 10.1016/j.padiff.2023.100519

  \item M.~Cugnet, F.~Gallois, A.~Kirchev and \textbf{D.~Dutykh}. \textit{NEOLAB: A Scilab tool to simulate the Negative Electrode of Lead-Acid Batteries}. SoftwareX, \textbf{22}, 101394, 2023 % No (HAL & Arxiv)
  % 10.1016/j.softx.2023.101394
  
  \item H.~Geoffroy, J.~Berger, B.~Colange, S.~Lespinats and \textbf{D.~Dutykh}. \textit{The use of dimensionality reduction techniques for fault detection and diagnosis in a AHU unit: critical assessment of its reliability}, J. Build. Perform. Simul., \textbf{16}(3), 249--267, 2023 % No (HAL & Arxiv & RG)
  % 10.1080/19401493.2022.2080864

  \item S.~Gasparin, J.~Berger, R.~Belarbi, \textbf{D.~Dutykh} and N.~Mendes. \textit{Solving parametric problems in building renovation with a spectral reduced-order method}, J. Build. Perform. Simul., \textbf{16}(2), 211--230, 2023 % No (HAL & Arxiv & RG) KU
  % 10.1080/19401493.2022.2126527

  %%% 2022: (9)

  \listpart{\centering\large\textbf{-- 2022 --}}
  
  \item M.~Loukili, \textbf{D.~Dutykh}, S.~Pincemin, K.~Kotrasova and N.~Abcha. \textit{Theoretical investigation applied to scattering water wave by rectangular submerged obstacle/and submarine trench}. Geosciences, \textbf{12}(10), 379, 2022 \\ % Yes (HAL) No - (Arxiv & RG)
  \url{https://hal.science/hal-03855065/}
  
  %%% KU starts here %%%
  
  \item A.~Machmudah, \textbf{D.~Dutykh} and S.~Parman. \textit{Coupled and synchronization models of rhythmic arm movement in planar plane}. Bioengineering, \textbf{9}(2), 385, 2022 % No (HAL & Arxiv)
  
  \item G.~Khakimzyanov, Z.~Fedotova and \textbf{D.~Dutykh}. \textit{Two-dimensional models of wave hydrodynamics with high accuracy dispersion relation. III. Linear analysis for an uneven bottom}. Computational Technologies, \textbf{27}(2), 37--53, 2022 % No (HAL & Arxiv)
  
  \item B.~Colange, L.~Vuillon, S.~Lespinats and \textbf{D.~Dutykh}. \textit{MING: an interpretative support method for visual exploration of multidimensional data}. Information Visualization, \textbf{21}(3), 246--269, 2022 % No (HAL & Arxiv)
  
  \item D.~Blackmore, Ya.~Prykarpatsky, M.~Prytula, \textbf{D.~Dutykh} and A.~Prykarpatsky. \textit{On the integrability of a new generalized Gurevich--Zybin dynamical system, its Hunter--Saxton type reduction and related mysterious symmetries}, Analysis and Mathematical Physics, \textbf{12}, 66, 2022 % No (HAL & Arxiv)
  
  \item \textbf{D.~Dutykh} and J.-L.~Verger-Gaugry. \textit{On a class of lacunary almost Newman polynomials modulo $p$ and density theorems}, Uniform Distribution Theory, \textbf{17}(1), 29--54, 2022 \\ % HAL & Arxiv
  \url{https://hal.archives-ouvertes.fr/hal-03517173/}
  
  \item A.~Machmudah, M.~Shanmugavel, S.~Parman, T.S.B. Abd Manan, \textbf{D.~Dutykh}, S.~Beddu and A.~Rajabi. \textit{Flight Trajectories Optimization of fixed-wing UAV by Bank-Turn Mechanism}, Drones, \textbf{6}(3), 69, 2022 % No (HAL & Arxiv)
  
  \item T.~Bueler-Faudree, S.~Delamere, \textbf{D.~Dutykh}, A.~Rybkin and A.~Suleimani. \textit{Fast shallow water-wave solver for plane inclined beaches}. SoftwareX, \textbf{17}, 100983, 2022 % No (HAL & Arxiv)
  
  \item A.~Rashidi, \textbf{D.~Dutykh}, N.K.~Farajkhah and L.~Audin. \textit{Regional tsunami hazard from splay faults in the Gulf of Oman}. Ocean Engineering, \textbf{243}, 110169, 2022 % No (HAL & Arxiv)

  %%% 2021: (11)
  \listpart{\centering\large\textbf{-- 2021 --}}
  
  \item O.~Gusev, G.~Khakimzyanov, L.~Chubarov and \textbf{D.~Dutykh}. \textit{Assessing the frequency dispersion influence on the solitary-wave interaction with a constant sloping beach}. Journal of Applied Mechanics and Technical Physics, \textbf{62}, 624--632, 2021 % No (HAL & Arxiv)
  
  \item M.~Loukili, \textbf{D.~Dutykh}, C.~Nadjib and K.~Kotrasova. \textit{Analytical and numerical investigations applied to study the reflection and transmission coefficients of wave-rectangular breakwater cited at the bottom of tank}. Geosciences, \textbf{11}(10), 430, 2021 % No (HAL & Arxiv)
  
  \item \textbf{D.~Dutykh} and J.-L.~Verger-Gaugry. \textit{Alphabets, rewriting trails and periodic representations in algebraic bases}. Res. number theory, \textbf{7}, 64, 2021 \\ % Arxiv + HAL
  \url{https://hal.archives-ouvertes.fr/hal-03090468/}
  
  \item T.S.B.~Abd Manan, S.~Beddu, N.L.~Mohd Kamal, D.~Mohamad, Z.~Itam, T.~Khan, A.~Machmudah, \textbf{D.~Dutykh}, W.H.M.~Wan~Mohtar, H.~Jusoh, F.~Mohamed Nazri, M.F.K.~Mohd~Yapandi, S.~Pati, A.~Ahmad and N.~Wan~Rasdi. \textit{Ecological risk indicators for leached heavy metals from coal ash generated at a Malaysian power plant}, Sustainability, \textbf{13}(18), 10222, 2021 % No (HAL, Arxiv)
  
  \item G.~Khakimzyanov, Z.~Fedotova and \textbf{D.~Dutykh}. \textit{Two-dimensional model of wave hydrodynamics with high accuracy dispersion relation. II. Fourth, sixth and eighth orders}, Computational Technologies, \textbf{26}(3), 4--25, 2021 % No (HAL, Arxiv)
  
  \item M.~Hunt and \textbf{D.~Dutykh}. \textit{Free surface flows in electrohydrodynamics with a constant vorticity distribution}, Water Waves, \textbf{3}, 297--317, 2021 \\ % Arxiv
  \url{https://hal.archives-ouvertes.fr/hal-02344438/}
  
  \item M.~Loukili, \textbf{D.~Dutykh}, K.~Kotrasova and D.~Ning. \textit{Numerical Stability Investigations of the Method of Fundamental Solutions Applied to Wave-Current Interactions Using Generating-Absorbing Boundary Conditions}. Symmetry, \textbf{13}(7), 1153, 2021 % No (HAL & Arxiv)
  
  \item A.~Cheviakov, \textbf{D.~Dutykh} and A.~Assylbekuly. \textit{On Galilean invariant and energy preserving BBM-type equations}. Symmetry, \textbf{13}(5), 878, 2021 % No (HAL & Arxiv)
  
  \item \textbf{D.~Dutykh} and H.~Le Meur. \textit{Derivation of a viscous Serre--Green--Naghdi equation: an impasse?} Fluids, \textbf{6}(4), 135, 2021 \\ % Arxiv
  \url{https://hal.archives-ouvertes.fr/hal-02414312/}
  
  \item M.~Loukili, K.~Kotrasova and \textbf{D.~Dutykh}. \textit{Numerical modeling of jet at the bottom of tank at moderate Reynolds number using compact Hermitian finite differences method}, Fluids, \textbf{6}(2), 63, 2021 % No (HAL & Arxiv)
  
  \item P.~Kundu, S.M.~Sarkar, A.~Rashidi and \textbf{D.~Dutykh}. \textit{Comparison of ground deformation by two infinite faults in different medium}, GEM --- Int. J. Geomath., \textbf{12}(3), 2021 % No (HAL & Arxiv)
  
  %%% 2020: (18)
  \listpart{\centering\large\textbf{-- 2020 --}}
  
  \item A.~Rashidi, \textbf{D.~Dutykh} and Z.H.~Shomali. \textit{Horizontal displacements effect in tsunami wave generation in the Western Makran region}, J. Ocean Eng. Mar. Energy, \textbf{6}, 427--439, 2020 % No (HAL & Arxiv)
  
  \item G.S.~Khakimzyanov, Z.I. Fedotova and \textbf{D.~Dutykh}. \textit{Two-dimensional model of wave hydrodynamics with high accuracy dispersion relation}, Computational Technologies, \textbf{25}(5), 17--41, 2020 % No (HAL, Arxiv) % http://www.ict.nsc.ru/jct/annotation/1993?l=eng
  
  \item D.~Mj (Sarkar) and \textbf{D.~Dutykh}. \textit{Learning extreme wave run-up conditions}. Applied Ocean Research, \textbf{105}, 102400, 2020 % No (HAL & Arxiv)
  
  \item S.H.~Shamsnia and \textbf{D.~Dutykh}. \textit{An analytical study on wave-current-mud interaction}, Water, \textbf{12}(10), 2899, 2020 % No (HAL & Arxiv)
  
  \item A.~Rashidi, \textbf{D.~Dutykh}, Z.H.~Shomali, N.K.~Farajkhah and M.~Nouri. \textit{A review of tsunami hazard in the Makran subduction zone}, Geosciences, \textbf{10}(9), 372, 2020 % No (HAL & Arxiv)
  
  \item A.~Abdalazeez, I.~Didenkulova, \textbf{D.~Dutykh} and P.~Denissenko. \textit{Comparison of dispersive and nondispersive models for modelling long wave run-up on a beach}, Izvestiya, Atmospheric and Oceanic Physics, \textbf{56}(5), 494--501, 2020 % No (HAL & Arxiv)
  
  \item G.~Sadaka and \textbf{D.~Dutykh}. \textit{Adaptive numerical modelling of tsunami wave generation and propagation with FreeFem++}, Geosciences, \textbf{10}(9), 351, 2020 \\ % No (Arxiv)
  \url{https://hal.archives-ouvertes.fr/hal-02912526/}
  
  \item A.~Abdalazeez, I.I.~Didenkulov, \textbf{D.~Dutykh} and P.~Denissenko. \textit{Comparison of Dispersive and Nondispersive Models for Wave Run-Up on a Beach}, Izv. Atmos. Ocean. Phys., \textbf{56}, 494--501, 2020 % No (HAL & Arxiv)
  
  \item \textbf{D.~Dutykh} and E.~Tobisch (Kartashova). \textit{Formation of the dynamic energy cascades in quartic and quintic generalized KdV equations}, Symmetry, \textbf{12}(8), 1254, 2020 \\ % No (Arxiv)
  \url{http://hal.archives-ouvertes.fr/hal-01070799/}
  
  \item A.~Abdalazeez, I.~Didenkulova, D.~\textbf{Dutykh} and C.~Labart. \textit{Extreme inundation statistics on a composite beach}, Water, \textbf{12}(6), 1573, 2020 \\ % Arxiv
  \url{https://hal.archives-ouvertes.fr/hal-02657270/}
  
  \item \textbf{D.~Dutykh} and E.~Tobisch (Kartashova). \textit{Resonance enhancement by suitably chosen frequency detuning}, Mathematics, \textbf{8}(3), 450, 2020 \\ % Arxiv
  \url{http://hal.archives-ouvertes.fr/hal-01084796/}
  
  \item J.~Berger, \textbf{D.~Dutykh}, N.~Mendes and L.~Gosse. \textit{An efficient numerical model for the simulation of coupled heat, air and moisture transfer in porous media}, Engineering Reports, \textbf{2}(2), e12099, 2020 \\ % No (Arxiv)
  \url{https://hal.archives-ouvertes.fr/hal-02413029/}
  
  \item J.~Berger, T.~Busser, T.~Colinart and \textbf{D.~Dutykh}. \textit{Critical assessment of a new mathematical model for hysteresis effects on heat and mass transfer in porous building material}, Int. J. Therm. Sci., \textbf{151}, 106275, 2020 \\ % No (Arxiv)
  \url{https://hal.archives-ouvertes.fr/hal-02485497/}
  
  \item A.~Rashidi, Z.H.~Shomali, \textbf{D.~Dutykh} and N.K.~Farajkhah. \textit{Tsunami hazard assessment in the Makran subduction zone}, Natural Hazards, \textbf{100}, 861--875, 2020 \\ % Arxiv
  \url{https://hal.archives-ouvertes.fr/hal-01737767/}
  
  \item I.~Abroug, N.~Abcha, \textbf{D.~Dutykh}, A.~Jarno and F.~Marin. \textit{Experimental and numerical study of the propagation of focused wave groups in the nearshore zone}, Phys. Lett. A, \textbf{384}(6), 126144, 2020 \\ % Arxiv
  \url{https://hal.archives-ouvertes.fr/hal-02362472/}
  
  \item J.~Berger, S.~Gasparin, \textbf{D.~Dutykh} and N.~Mendes. \textit{On the comparison of three numerical methods applied to building simulation: finite-differences, RC circuit approximation and a spectral method}, Building Simulation, \textbf{13}(1), 1--18, 2020 \\ % Arxiv
  \url{https://hal.archives-ouvertes.fr/hal-02140325/}
  
  \item G.~Khakimzyanov and \textbf{D.~Dutykh}. \textit{Long wave interaction with a partially immersed body. Part I: Mathematical models}, Commun. Comput. Phys., \textbf{27}(2), 321--378, 2020 \\ % Arxiv
  \url{https://hal.archives-ouvertes.fr/hal-02070055/}
  
  \item S.~Rusconi, \textbf{D.~Dutykh}, A.~Zarnescu, D.~Sokolovski and E.~Akhmatskaya. \textit{An optimal scaling to computationally tractable dimensionless models: Study of latex particles morphology formation}, Comput. Phys. Commun., \textbf{247}, 106944, 2020 \\ % Arxiv
  \url{https://hal.archives-ouvertes.fr/hal-02301950/}
  
  %%% 2019: (20)
  \listpart{\centering\large\textbf{-- 2019 --}}
  
  \item A.~Abdalazeez, I.~Didenkulova and \textbf{D.~Dutykh}. \textit{Nonlinear deformation and run-up of single tsunami waves of positive polarity: numerical simulations and analytical predictions}, Nat. Hazards Earth Syst. Sci., \textbf{19}, 2905--2913, 2019 \\ % Arxiv
  \url{https://hal.archives-ouvertes.fr/hal-02422302/}
  
  \item \textbf{D.~Dutykh}. \textit{Numerical simulation of Feller's diffusion equation}, Mathematics, \textbf{7}(11), 1067, 2019 \\ % Arxiv
  \url{https://hal.archives-ouvertes.fr/hal-02290284/}
  
  \item D.~Clamond, \textbf{D.~Dutykh} and D.~Mitsotakis. \textit{Hamiltonian regularisation of shallow water equations with uneven bottom}, J. Phys. A: Math. Theor., \textbf{52}(42), 42LT01, 2019 \\ % Arxiv
  \url{https://hal.archives-ouvertes.fr/hal-02140161/}
  
  \item J.~Berger and \textbf{D.~Dutykh}. \textit{Evaluation of the reliability of building energy performance models for parameter estimation}, Comput. Technologies, \textbf{24}(3), 4--32, 2019 \\ % Arxiv
  \url{https://hal.archives-ouvertes.fr/hal-02140452/}
  
  \item M.~Abdykarim, J.~Berger, \textbf{D.~Dutykh}, L.~Soudani and A.~Agbossou. \textit{Critical assessment of efficient numerical methods for a long-term simulation of heat and moisture transfer in porous materials}, Int. J. Therm. Sci., \textbf{145}, 105982, 2019 \\ % No (Arxiv)
  \url{https://hal.archives-ouvertes.fr/hal-02162803/}
  
  \item D.~Mitsotakis, Q.~Li, E.~Peach and \textbf{D.~Dutykh}. \textit{On some model equations for pulsatile flow in viscoelastic vessels}, Wave Motion, \textbf{90}, 139--151, 2019 \\ % Arxiv
  \url{https://hal.archives-ouvertes.fr/hal-02135521/}
  
  \item A.~Dur\'{a}n, \textbf{D.~Dutykh} and D.~Mitsotakis. \textit{On the multi-symplectic structure of Boussinesq-type systems. II: Geometric discretization}, Phys. D, \textbf{397}, 1--16, 2019 \\ % Arxiv
  \url{https://hal.archives-ouvertes.fr/hal-02123559/}
  
  \item \textbf{D.~Dutykh} and D.~Ionescu-Kruse. \textit{Effects of vorticity on the travelling waves of some shallow water two-component systems}, Discrete \& Continuous Dynamical Systems --- A, \textbf{39}(9), 5521--5541, 2019 \\ % Arxiv
  \url{https://hal.archives-ouvertes.fr/hal-02094922/}
  
  \item G.~Khakimzyanov, \textbf{D.~Dutykh}, D.~Mitsotakis and N.~Shokina. \textit{Numerical simulation of conservation laws with moving grid nodes: Application to tsunami wave modelling}, Geosciences, \textbf{9}(5), 197, 2019 \\ % Arxiv
  \url{https://hal.archives-ouvertes.fr/hal-01223510/}

  \item E.~Dinvay, \textbf{D.~Dutykh} and H.~Kalisch. \textit{A comparative study of bi-directional Whitham systems}, Appl. Numer. Math., \textbf{141}, 248--262, 2019 \\ % Arxiv
  \url{https://hal.archives-ouvertes.fr/hal-02020212/}
  
  \item J.-G. Caputo, \textbf{D.~Dutykh} and B.~Gleyse. \textit{Coupling conditions for water waves at forks}, Symmetry, \textbf{11}(3), 434, 2019 \\ % Arxiv
  \url{https://hal.archives-ouvertes.fr/hal-01206504/}
  
  \item J.~Berger, T.~Busser, \textbf{D.~Dutykh} and N.~Mendes. \textit{An efficient method to estimate sorption isotherm curve coefficients},  Inv. Prob. Sci. and Eng., \textbf{27}(6), 735--772, 2019 \\ % Arxiv
  \url{https://hal.archives-ouvertes.fr/hal-01509113/}
  
  \item A.~Jumabekova, J.~Berger, \textbf{D.~Dutykh}, H.~Le~Meur, A.~Foucquier, M.~Pailha and Ch.~M\'en\'ezo. \textit{An efficient numerical model for liquid water uptake in porous material and its parameter estimation}, Numerical Heat Transfer, Part A: Applications, \textbf{75}(2), 110--136, 2019 \\ % Arxiv
  \url{https://hal.archives-ouvertes.fr/hal-02047087/}
  
  \item J.-P.~Chehab and \textbf{D.~Dutykh}. \textit{On time relaxed schemes and formulations for dispersive wave equations}, AIMS Mathematics, \textbf{4}(2), 254--278, 2019 \\ % Arxiv
  \url{https://hal.archives-ouvertes.fr/hal-02057433/}
  
  \item V.~Liapidevskii and \textbf{D.~Dutykh}. \textit{On the velocity of turbidity currents over moderate slopes}, Fluid Dyn. Res., \textbf{51}, 035501, 2019 \\ % Arxiv
  \url{https://hal.archives-ouvertes.fr/hal-01719313/}
  
  \item S.~Gasparin, J.~Berger, \textbf{D.~Dutykh} and N.~Mendes. \textit{An innovative method to determine optimum insulation thickness based on non-uniform adaptive moving grid}, Journal of the Brazilian Society of Mechanical Sciences and Engineering, \textbf{41}:173, 2019 \\ % Arxiv
  \url{https://hal.archives-ouvertes.fr/hal-02045015/}
  
  \item S.~Gasparin, \textbf{D.~Dutykh} and N.~Mendes. \textit{A spectral method for solving heat and moisture transfer through consolidated porous media}, Int. J. Numer. Meth. Eng., \textbf{117}(11), 1143--1170, 2019 \\ % Arxiv
  \url{https://hal.archives-ouvertes.fr/hal-02023462/}
  
  \item J.~Berger, \textbf{D.~Dutykh}, N.~Mendes and B.~Rysbaiuly. \textit{A new model for simulating heat, air and moisture transport in porous building materials}, Int. J. Heat Mass Transf., \textbf{134}, 1041--1060, 2019 \\ % Arxiv
  \url{https://hal.archives-ouvertes.fr/hal-02052022/}
  
  \item S.~Gasparin, J.~Berger, \textbf{D.~Dutykh} and N.~Mendes. \textit{Solving nonlinear diffusive problems in buildings by means of a reduced spectral method}, J. of Build. Perf. Sim., \textbf{12}(1), 17--36, 2019 \\ % Arxiv
  \url{https://hal.archives-ouvertes.fr/hal-01513304/}
  
  \item A.~Dur\'an, \textbf{D.~Dutykh} and D.~Mitsotakis. \textit{On the multi-symplectic structure of Boussinesq-type systems. I: Derivation and mathematical properties}, Phys.~D, \textbf{388}, 10--21, 2019 \\ % Arxiv
  \url{https://hal.archives-ouvertes.fr/hal-01930748/}

  %%% 2018: (22)
  \listpart{\centering\large\textbf{-- 2018 --}}
  
  \item \textbf{D.~Dutykh} and J.-L. Verger-Gaugry. \textit{On the reducibility and the lenticular sets of zeroes of almost Newman lacunary polynomials}, Arnold Mathematical Journal, \textbf{4}(3-4), 315--344, 2018 \\ % Arxiv
  \url{https://hal.archives-ouvertes.fr/hal-02045588/}
  
  \item Y.~Pu, R.L.~Pego, \textbf{D.~Dutykh} and D.~Clamond. \textit{Weakly singular shock profiles for a non-dispersive regularization of shallow-water equations}, Comm. Math. Sci., \textbf{16}(5), 1361--1378, 2018 \\ % Arxiv
  \url{https://hal.archives-ouvertes.fr/hal-01794005/}
  
  \item S.~Gasparin, J.~Berger, \textbf{D.~Dutykh} and N.~Mendes. \textit{An adaptive simulation of nonlinear heat and moisture transfer as a boundary value problem}, Int. J. Therm. Sci., \textbf{133}, 120--139, 2018 \\ % Arxiv
  \url{https://hal.archives-ouvertes.fr/hal-02021293/}

  \item S.~Gasparin, J.~Berger, \textbf{D.~Dutykh} and N.~Mendes. \textit{Advanced reduced-order models for moisture diffusion in porous media}, Transport in Porous Media, \textbf{124}(3), 965--994, 2018 \\ % Arxiv
  \url{https://hal.archives-ouvertes.fr/hal-01522319/}
  
  \item A.~Rashidi, Z.H.~Shomali, \textbf{D.~Dutykh} and N.K.~Farajkhah. \textit{Evaluation of tsunami wave energy generated by earthquakes in the Makran subduction zone}, Ocean Eng., \textbf{165}(1), 131--139, 2018 \\ % Arxiv
  \url{https://hal.archives-ouvertes.fr/hal-01719939/}

  \item \textbf{D.~Dutykh}, M.~Hoefer and D.~Mitsotakis. \textit{Solitary wave solutions and their interactions for fully nonlinear water waves with surface tension in the generalized Serre equations}. Theor. Comp. Fluid Dyn., \textbf{32}(3), 371--397, 2018 \\ % Arxiv
  \url{https://hal.archives-ouvertes.fr/hal-01465356/}

  \item J.~Berger, H.~Le Meur, \textbf{D.~Dutykh}, D. M. Nguyen and A.-C. Grillet. \textit{Analysis and improvement of the VTT mold growth model: application to bamboo fiberboard}, Building and Environment, \textbf{138}, 262--274, 2018 \\ % Arxiv
  \url{https://hal.archives-ouvertes.fr/hal-01759837/}

  \item \textbf{D.~Dutykh} and J.-G. Caputo. \textit{Wave dynamics on networks: method and application to the sine--Gordon equation}, Appl. Numer. Math., \textbf{131}, 54--71, 2018 \\ % Arxiv
  \url{https://hal.archives-ouvertes.fr/hal-01160840/}
  
  \item D.~Mitsotakis, \textbf{D.~Dutykh} and Q.~Li. \textit{Asymptotic nonlinear and dispersive pulsatile flow in elastic vessels with cylindrical symmetry}, Computers \& Mathematics with Applications, \textbf{75}, 4022--4047, 2018 \\ % Arxiv
  \url{https://hal.archives-ouvertes.fr/hal-01756720/}

  \item D.~Clamond and \textbf{D.~Dutykh}. \textit{Accurate fast computation of steady two-dimensional surface gravity waves in arbitrary depth}. J. Fluid Mech., \textbf{844}, 491--518, 2018 \\ % Arxiv
  \url{https://hal.archives-ouvertes.fr/hal-01465813/}

  \item J.~Berger, S.~Gasparin, \textbf{D.~Dutykh} and N.~Mendes. \textit{On the solution of coupled heat and moisture transport in porous material}, Transport in Porous Media, \textbf{121}(3), 665--702, 2018 \\ % Arxiv
  \url{https://hal.archives-ouvertes.fr/hal-01770386/}

  \item S.~Gasparin, J.~Berger, \textbf{D.~Dutykh} and N.~Mendes. \textit{An improved explicit scheme for whole-building hygrothermal simulation}, Building Simulation, \textbf{11}(3), 465--481, 2018 \\ % Arxiv
  \url{https://hal.archives-ouvertes.fr/hal-01495737/}
  
  \item V.~Liapidevskii, \textbf{D.~Dutykh} and M.~Gisclon. \textit{On the modelling of shallow turbidity flows}, Adv. Water Resour., \textbf{113}, 310--327, 2018 \\ % Arxiv
  \url{https://hal.archives-ouvertes.fr/hal-01514095/}

  \item G.~Khakimzyanov and \textbf{D.~Dutykh}. \textit{Numerical modelling of surface water wave interaction with a moving wall}, Commun. Comput. Phys., \textbf{23}(5), 1289--1354, 2018 \\ % Arxiv
  \url{https://hal.archives-ouvertes.fr/hal-01546833/}

  \item S.~Gasparin, J.~Berger, \textbf{D.~Dutykh} and N.~Mendes. \textit{Stable explicit schemes for simulation of nonlinear moisture transfer in porous materials}. J. of Build. Perf. Sim., \textbf{11}(2), 129--144, 2018 \\ % Arxiv
  \url{https://hal.archives-ouvertes.fr/hal-01404578/}

  \item J.~Berger, T.~Busser, \textbf{D.~Dutykh} and N.~Mendes. \textit{On the estimation of moisture permeability and advection coefficients of a wood fibre material using the optimal experiment design approach}, Experimental Thermal and Fluid Science, \textbf{90}, 246--259, 2018 \\ % Arxiv
  \url{https://hal.archives-ouvertes.fr/hal-01498638/}
  
  \item L.~Vuillon, \textbf{D.~Dutykh} and F.~Fedele. \textit{Some special solutions to the Hyperbolic NLS equation}, Comm. Nonlinear Sci. Numer. Simulat., \textbf{57}, 202--220, 2018 \\ % Arxiv
  \url{http://hal.archives-ouvertes.fr/hal-00846801/}

  \item G.~Khakimzyanov, \textbf{D.~Dutykh} and O.~Gusev. \textit{Dispersive shallow water wave modelling. Part IV: Numerical simulation on a globally spherical geometry}, Commun. Comput. Phys., \textbf{23}(2), 361--407, 2018 \\ % Arxiv
  \url{https://hal.archives-ouvertes.fr/hal-01558680/}

  \item G.~Khakimzyanov, \textbf{D.~Dutykh} and Z.~Fedotova. \textit{Dispersive shallow water wave modelling. Part III: Model derivation on a globally spherical geometry}, Commun. Comput. Phys., \textbf{23}(2), 315--360, 2018 \\ % Arxiv
  \url{https://hal.archives-ouvertes.fr/hal-01552229/}

  \item G.~Khakimzyanov, \textbf{D.~Dutykh}, O.~Gusev and N.~Shokina. \textit{Dispersive shallow water wave modelling. Part II: Numerical simulation on a globally flat space}, Commun. Comput. Phys., \textbf{23}(1), 30--92, 2018 \\ % Arxiv
  \url{https://hal.archives-ouvertes.fr/hal-01551075/}

  \item G.~Khakimzyanov, \textbf{D.~Dutykh}, Z.~Fedotova and D.~Mitsotakis. \textit{Dispersive shallow water wave modelling. Part I: Model derivation on a globally flat space}, Commun. Comput. Phys., \textbf{23}(1), 1--29, 2018 \\ % Arxiv
  \url{https://hal.archives-ouvertes.fr/hal-01547833/}
  
  \item D.~Clamond and \textbf{D.~Dutykh}. \textit{Non-dispersive conservative regularisation of nonlinear shallow water and isothermal Euler equations}, Commun. Nonlinear Sci. Numer. Simulat., \textbf{55}, 237--247, 2018 \\ % Arxiv
  \url{https://hal.archives-ouvertes.fr/hal-01509445/}
  
  %%% 2017: (9)
  \listpart{\centering\large\textbf{-- 2017 --}}
  
  \item G.~Khakimzyanov and \textbf{D.~Dutykh}. \textit{On supraconvergence phenomenon for second order centered finite differences on non-uniform grids}, J. Comp. Appl. Math., \textbf{326}, 1--14, 2017 \\ % Arxiv
  \url{https://hal.archives-ouvertes.fr/hal-01223522/}

  \item M.~Chhay, \textbf{D.~Dutykh}, M.~Gisclon and Ch.~Ruyer-Quil. \textit{New asymptotic heat transfer model in thin liquid films}, Appl. Math. Model., \textbf{48}, 844--859, 2017 \\ % Arxiv
  \url{https://hal.archives-ouvertes.fr/hal-01224182/}
  
  \item D.~Mitsotakis, \textbf{D.~Dutykh}, A.~Assylbekuly and D.~Zhakebayev. \textit{On weakly singular and fully nonlinear travelling shallow capillary-gravity waves in the critical regime}, Phys. Lett. A, \textbf{381}(20), 1719--1726, 2017 \\ % Arxiv
  \url{https://hal.archives-ouvertes.fr/hal-01388481/}
  
  \item J.~Berger, S.~Gasparin, \textbf{D.~Dutykh} and N.~Mendes. \textit{Accurate numerical simulation of moisture front in porous material}, Building and Environment, \textbf{118}, 211--224, 2017 \\ % Arxiv
  \url{https://hal.archives-ouvertes.fr/hal-01419018/}
  
  \item E.~Dinvay, D.~Moldabayev, \textbf{D.~Dutykh} and H.~Kalisch. \textit{The Whitham equation with surface tension}, Nonlinear Dynamics, \textbf{88}(2), 1125--1138, 2017 \\ % Arxiv
  \url{https://hal.archives-ouvertes.fr/hal-01504047/}

  \item D.~Mitsotakis, \textbf{D.~Dutykh} and J.~Carter. \textit{On the nonlinear dynamics of the traveling-wave solutions of the Serre equations}, Wave Motion, \textbf{70}, 166--182, 2017 \\ % Arxiv
  \url{http://hal.archives-ouvertes.fr/hal-00984035/}

  \item \textbf{D.~Dutykh}, D.~Clamond and M.~Chhay. \textit{Serre-type equations in deep water}, Math. Model. Nat. Phenom., \textbf{12}(1), 23--40, 2017 \\ % Arxiv
  \url{https://hal.archives-ouvertes.fr/hal-01340379/}

  \item D.~Clamond, \textbf{D.~Dutykh} and D.~Mitsotakis. \textit{Conservative modified Serre--Green--Naghdi equations with improved dispersion characteristics}, Comm. Nonlinear Sci. Numer. Simul., \textbf{45}, 245--257, 2017 \\ % Arxiv
  \url{https://hal.archives-ouvertes.fr/hal-01232370/}

  \item J.~Berger, \textbf{D.~Dutykh} and N.~Mendes. \textit{On the optimal experimental design for heat and moisture parameter estimation}, Experimental Thermal and Fluid Science, \textbf{81}, 109--122, 2017 \\ % Arxiv
  \url{https://hal.archives-ouvertes.fr/hal-01334414/}
  
  %%% 2016: (9)
  \listpart{\centering\large\textbf{-- 2016 --}}

  \item \textbf{D.~Dutykh} and D.~Clamond. \textit{Modified Shallow Water Equations for significantly varying seabeds}. Appl. Math. Modelling, \textbf{40}(23-24), 9767--9787, 2016 \\ % Arxiv
  \url{http://hal.archives-ouvertes.fr/hal-00675209/}

  \item D.~Clamond, \textbf{D.~Dutykh} and A.~Galligo. \textit{Algebraic method for constructing singular steady solitary waves: A case study}, Proc. R. Soc. A., \textbf{472}(2191), 20160194, 2016 \\ % Arxiv
  \url{https://hal.archives-ouvertes.fr/hal-01290471/}
  
  \item D.~Clamond and \textbf{D.~Dutykh}. \textit{Multi-symplectic structure of fully-nonlinear weakly-dispersive internal gravity waves}, J. Phys. A: Math. Theor., \textbf{49}, 31LT01, 2016 \\ % Arxiv
  \url{https://hal.archives-ouvertes.fr/hal-01296552/}

  \item \textbf{D.~Dutykh}, D.~Clamond and A.~Dur\'an. \textit{Efficient computation of capillary-gravity generalized solitary waves}, Wave Motion, \textbf{65}, 1--16, 2016 \\ % Arxiv
  \url{https://hal.archives-ouvertes.fr/hal-01218989/}
  
  \item \textbf{D.~Dutykh} and D.~Ionescu--Kruse. \textit{Travelling wave solutions for some two-component shallow water models}, J. Diff. Equations, \textbf{261}(2), 1099--1114, 2016 \\ % No (Arxiv)
  \url{https://hal.archives-ouvertes.fr/hal-01294603/}
  
  \item \textbf{D.~Dutykh} and O.~Goubet. \textit{Derivation of dissipative Boussinesq equations using the Dirichlet-to-Neumann operator approach}, Math. Comput. Simul., \textbf{127}, 80--93, 2016 \\ % Arxiv
  \url{http://hal.archives-ouvertes.fr/hal-00596804/}
  
  \item F.~Carbone, \textbf{D.~Dutykh} and G.~El. \textit{Macroscopic dynamics of incoherent soliton ensembles: soliton-gas kinetics and direct numerical modeling: Incoherent soliton ensembles}, EPL, \textbf{113}, 30003, 2016 \\ % Arxiv
  \url{https://hal.archives-ouvertes.fr/hal-01248680/}
  
  \item M.~Chhay, \textbf{D.~Dutykh} and D.~Clamond. \textit{On the multi-symplectic structure of the Serre--Green--Naghdi equations}, J. Phys. A: Math. Theor., \textbf{49}, 03LT01, 2016 \\ % Arxiv
  \url{https://hal.archives-ouvertes.fr/hal-01221356/}
  
  \item G.~Khakimzyanov, N.~Shokina, \textbf{D.~Dutykh} and D.~Mitsotakis. \textit{A new run-up algorithm based on local high-order analytic expansions}, J. Comp. Appl. Math., \textbf{298}, 82--96, 2016 \\ % Arxiv
  \url{http://hal.archives-ouvertes.fr/hal-01084811/}
  
  %%% 2015: (8)
  \listpart{\centering\large\textbf{-- 2015 --}}
  
  \item A.~Rafiee, \textbf{D.~Dutykh} and F.~Dias. \textit{Numerical simulation of wave impact on a rigid wall using a two-phase compressible SPH method}. Procedia IUTAM, \textbf{18}, 123--137, 2015 \\ % Arxiv
  \url{http://hal.archives-ouvertes.fr/hal-00830054/}

  \item D.~Clamond, \textbf{D.~Dutykh} and A.~Dur\'an. \textit{A plethora of generalised solitary gravity-capillary water waves}, J. Fluid Mech., \textbf{784}, 664--680, 2015 \\ % Arxiv
  \url{http://hal.archives-ouvertes.fr/hal-01081798/}
  % 10.1017/jfm.2015.616
  
  \item H.~Nersisyan, \textbf{D.~Dutykh} and E.~Zuazua. \textit{Generation of 2D water waves by moving bottom disturbances}. IMA J. Appl. Math., \textbf{80}(4), 1235--1253, 2015 \\ % Arxiv
  \url{http://hal.archives-ouvertes.fr/hal-00752364/}
  
  \item D.~Moldabayev, H.~Kalisch and \textbf{D.~Dutykh}. \textit{The Whitham equation as a model for surface water waves}, Phys. D, \textbf{309}, 99--107, 2015 \\ % Arxiv
  \url{http://hal.univ-savoie.fr/hal-01136855/}
  
  \item \textbf{D.~Dutykh}, D.~Clamond and D.~Mitsotakis. \textit{Adaptive modeling of shallow fully nonlinear gravity waves}, RIMS K\^oky\^uroku, \textbf{1947}, 45--65, 2015 \\ % Arxiv
  \url{https://hal.archives-ouvertes.fr/hal-01088440/}
  
  \item \textbf{D.~Dutykh}, D.~Clamond and M.~Chhay. \textit{Numerical study of the generalised Klein--Gordon equations}, Phys. D, \textbf{304--305}, 23--33, 2015 \\ % Arxiv
  \url{http://hal.archives-ouvertes.fr/hal-00851030/}
  
  \item \textbf{D.~Dutykh} and E.~Tobisch (Kartashova). \textit{Direct dynamical energy cascade in the modified KdV equation}, Phys. D, \textbf{297}, 76--87, 2015 \\ % Arxiv
  \url{http://hal.archives-ouvertes.fr/hal-00990724/}

  \item T.~Stefanakis, S.~Xu, \textbf{D.~Dutykh} and F.~Dias. \textit{Run-up amplification of transient long waves}. Quart. Appl. Math., LXXIII(1), 177--199, 2015 \\ % Arxiv
  \url{http://hal.archives-ouvertes.fr/hal-00768597/}

  %%% 2014: (12)
  \listpart{\centering\large\textbf{-- 2014 --}}

  \item I.~S.~Gandzha, Yu.~V.~Sedletsky and \textbf{D.~Dutykh}. \textit{High-order nonlinear Schr\"odinger equation for the envelope of slowly modulated gravity waves on the surface of finite-depth fluid and its quasi-soliton solutions}. Ukr. J. Phys., \textbf{59}(12), 1201--1215, 2014 \\ % Arxiv (ownership requested)
  \url{https://hal.archives-ouvertes.fr/hal-01084747/}
  
  \item \textbf{D.~Dutykh} and E.~Pelinovsky. \textit{Numerical simulation of a solitonic gas in some integrable and non-integrable models}, Phys. Lett. A, \textbf{378}(42), 3102--3110, 2014 \\ % Arxiv
  \url{http://hal.archives-ouvertes.fr/hal-00913960/}
  
  \item J.-G.~Caputo and \textbf{D.~Dutykh}. \textit{Nonlinear waves in networks: a simple approach using the sine--Gordon equation}, Phys. Rev. E, \textbf{90}, 022912, 2014 \\ % Arxiv
  \url{http://hal.archives-ouvertes.fr/hal-00951705/}
  
  \item D.~Mitsotakis, B.~Ilan and \textbf{D.~Dutykh}. \textit{On the Galerkin / finite-element method for the Serre equations}. J. Sci. Comp., \textbf{61}(1), 166--195, 2014 \\ % Arxiv
  \url{http://hal.archives-ouvertes.fr/hal-00834064/}
  
  \item \textbf{D.~Dutykh} and E.~Tobisch (Kartashova). \textit{Observation of the Inverse Energy Cascade in the modified Korteweg--de Vries Equation}, Eur.~Phys.~Lett., \textbf{107}, 14001, 2014 \\ % Arxiv
  \url{http://hal.archives-ouvertes.fr/hal-00991944/}
  
  \item Z.I.~Fedotova, G.S.~Khakimzyanov and \textbf{D.~Dutykh}. \textit{Energy equation for certain approximate models of long-wave hydrodynamics}, Russian Journal of Numerical Analysis and Mathematical Modelling, \textbf{29}(3), 167--178, 2014 \\ % No (Arxiv)
  \url{https://hal.archives-ouvertes.fr/hal-00998927/}
  
  \item M.~Hunt and \textbf{D.~Dutykh}. \textit{Visco-potential flows in electrohydrodynamics}, Phys.~Lett.~A, \textbf{378}, 1721--1726, 2014 \\ % Arxiv
  \url{http://hal.archives-ouvertes.fr/hal-00908724/}
  
  \item F.~Dias, \textbf{D.~Dutykh}, L.~O'Brien, E.~Renzi and T.~Stefanakis. \textit{On the modelling of tsunami generation and tsunami inundation}, Procedia IUTAM, \textbf{10}, 338--355, 2014 \\ % Arxiv
  \url{http://hal.archives-ouvertes.fr/hal-00728725/}
  
  \item C.~Viotti, \textbf{D.~Dutykh} and F.~Dias. \textit{The conformal-mapping method for surface gravity waves in the presence of variable bathymetry and mean current}, Procedia IUTAM, \textbf{11}, 110--118, 2014 \\ % No (Arxiv)
  \url{http://hal.archives-ouvertes.fr/hal-00855780/}
  
  \item \textbf{D.~Dutykh}. \textit{Evolution of random wave fields in the water of finite depth}. Procedia IUTAM, \textbf{11}, 34--43, 2014 \\ % Arxiv
  \url{http://hal.archives-ouvertes.fr/hal-00864549/}
  
  \item F.~Fedele and \textbf{D.~Dutykh}. \textit{Camassa--Holm equations and vortexons for axisymmetric pipe flows}. Fluid Dyn. Res., \textbf{46}, 015503, 2014 \\ % Arxiv
  \url{http://hal.archives-ouvertes.fr/hal-00759444/}

  \item \textbf{D.~Dutykh} and D.~Clamond. \textit{Efficient computation of steady solitary gravity waves}. Wave Motion, \textbf{51}, 86--99, 2014 \\ % Arxiv
  \url{http://hal.archives-ouvertes.fr/hal-00786077/}
  % 10.1016/j.wavemoti.2013.06.007

  %%% 2013: (11)
  \listpart{\centering\large\textbf{-- 2013 --}}

  \item F.~Fedele and \textbf{D.~Dutykh}. \textit{Camassa--Holm type equations for axisymmetric Poiseuille pipe flows}. Procedia IUTAM, \textbf{9}, 16--24, 2013 \\ % Arxiv
  \url{http://hal.archives-ouvertes.fr/hal-00752999/}

  \item F.~Carbone, \textbf{D.~Dutykh}, J.~Dudley and F.~Dias. \textit{Extreme wave runup on a vertical cliff}. Geophys. Res. Lett., \textbf{40}(12), 3138--3143, 2013 \\ % Arxiv
  \url{http://hal.archives-ouvertes.fr/hal-00799118/}

  \item A.~Dur\'an, \textbf{D.~Dutykh} and D.~Mitsotakis. \textit{On the Galilean invariance of some dispersive wave equations}, Stud. Appl. Math., \textbf{131}(4), 359--388, 2013 \\ % Arxiv
  \url{http://hal.archives-ouvertes.fr/hal-00664143/}

  \item \textbf{D.~Dutykh}, D.~Clamond, P.~Milewski and D.~Mitsotakis. \textit{Finite volume and pseudo-spectral schemes for the fully nonlinear 1D Serre equations}, European Journal of Applied Mathematics, \textbf{24}(5), 761--787, 2013 \\ % Arxiv
  \url{http://hal.archives-ouvertes.fr/hal-00587994/}
  
  \item D.~Clamond and \textbf{D.~Dutykh}. \textit{Fast accurate computation of the fully nonlinear solitary surface gravity waves}. Computers \& Fluids, \textbf{84}, 35--38, 2013 \\ % Arxiv
  \url{http://hal.archives-ouvertes.fr/hal-00759812/}
  % 10.1016/j.compfluid.2013.05.010
  
  \item C.~Viotti, \textbf{D.~Dutykh}, J.~Dudley and F.~Dias. \textit{Emergence of coherent wave groups in deep-water random sea}. Phys. Rev. E, \textbf{87}(6), 063001, 2013 \\ % No (Arxiv)
  \url{http://hal.archives-ouvertes.fr/hal-00795397/}
  
  \item \textbf{D.~Dutykh} and H.~Kalisch. \textit{Boussinesq modeling of surface waves due to underwater landslides}, Nonlin. Processes Geophys., \textbf{20}, 267--285, 2013 \\ % Arxiv
  \url{http://hal.archives-ouvertes.fr/hal-00654386/}

  \item F.~Fedele and \textbf{D.~Dutykh}. \textit{Vortexons in axisymmetric Poiseuille pipe flows}. Eur.~Phys.~Lett., \textbf{101}(3), 34003, 2013 \\ % Arxiv
  \url{http://hal.archives-ouvertes.fr/hal-00756531/}
  
  \item \textbf{D.~Dutykh}, F.~Fedele and M.~Chhay. \textit{Geometric numerical schemes for the KdV equation}. Computational Mathematics and Mathematical Physics, \textbf{53}(2), 221--236, 2013 \\ % Arxiv
  \url{http://hal.archives-ouvertes.fr/hal-00694896/}
  
  \item \textbf{D.~Dutykh}, D.~Mitsotakis, X.~Gardeil and F.~Dias. \textit{On the use of finite fault solution for tsunami generation problems}. Theor. Comput. Fluid Dyn., \textbf{27}, 177--199, 2013 \\ % Arxiv
  \url{http://hal.archives-ouvertes.fr/hal-00509384/}

  \item \textbf{D.~Dutykh}, Th.~Katsaounis and D.~Mitsotakis. \textit{Finite volume methods for unidirectional dispersive wave models}. Int. J. Num. Meth. Fluids, \textbf{71}, 717--736, 2013 \\ % Arxiv
  \url{http://hal.archives-ouvertes.fr/hal-00538043/}
  
  %%% 2012: (5)
  \listpart{\centering\large\textbf{-- 2012 --}}

  \item F.~Fedele and \textbf{D.~Dutykh}. \textit{Special solutions to a compact equation for deep-water gravity waves}. J. Fluid Mech., \textbf{712}, 646--660, 2012 \\ % Arxiv
  \url{http://hal.archives-ouvertes.fr/hal-00687325/}

  \item \textbf{D.~Dutykh}, D.~Mitsotakis, L.~Chubarov and Yu.~Shokin. \textit{On the contribution of the horizontal sea-bed displacements into the tsunami generation process}. Ocean Modelling, \textbf{56}, 43--56, 2012 \\ % Arxiv
  \url{http://hal.archives-ouvertes.fr/hal-00530999/}
  
 \item F.~Fedele and \textbf{D.~Dutykh}. \textit{Solitary wave interaction in a compact equation for deep-water gravity waves}. JETP Letters, \textbf{95}(12), 703--706, 2012 \\ % Arxiv
  \url{http://hal.archives-ouvertes.fr/hal-00687668/}

  \item S.A.~Beisel, L.B.~Chubarov, \textbf{D.~Dutykh}, G.S.~Khakimzyanov and N.Yu.~Shokina. \textit{Simulation of surface waves generated by an underwater landslide in a bounded reservoir}. Russ. J. Numer. Anal. Math. Modelling, \textbf{27}(6), 539--558, 2012 \\ % No (Arxiv)
  \url{http://hal.archives-ouvertes.fr/hal-00788284/}

  \item D.~Clamond and \textbf{D.~Dutykh}. \textit{Practical use of variational principles for modeling water waves}. Physica D, \textbf{241}(1), 25--36, 2012 \\ % Arxiv
  \url{http://hal.archives-ouvertes.fr/hal-00456891/}

  %%% 2011: (7)
  \listpart{\centering\large\textbf{-- 2011 --}}

  \item F.~Fedele and \textbf{D.~Dutykh}. \textit{Hamiltonian form and solitary waves of the spatial Dysthe equations}. JETP Letters, \textbf{94}(12), 921--925, 2011 \\ % Arxiv
  \url{http://hal.archives-ouvertes.fr/hal-00633389/}

  \item \textbf{D.~Dutykh}, C.~Labart and D.~Mitsotakis. \textit{Long wave runup on random beaches}. Phys. Rev. Lett., \textbf{107}, 184504, 2011 \\ % Arxiv
  \url{http://hal.archives-ouvertes.fr/hal-00606627/}
  
  \item T.~Stefanakis, F.~Dias and \textbf{D.~Dutykh}. \textit{Local Run-Up Amplification by Resonant Wave Interactions}. Phys. Rev. Lett., \textbf{107}, 124502, 2011 \\ % Arxiv
  \url{http://hal.archives-ouvertes.fr/hal-00605461/}
  
  \item \textbf{D.~Dutykh} and D.~Clamond. \textit{Shallow water equations for large bathymetry variations}, J. Phys. A: Math. Theor. \textbf{44}, 332001, 2011 \\ % Arxiv
  \url{http://hal.archives-ouvertes.fr/hal-00580310/}
      
  \item \textbf{D.~Dutykh}, C.~Acary-Robert and D.~Bresch. \textit{Mathematical modeling of powder-snow avalanche flows}. Studies in Applied Mathematics, \textbf{127}(1), 38--66, 2011 \\ % Arxiv
  \url{http://hal.archives-ouvertes.fr/hal-00354000/}

  \item \textbf{D.~Dutykh}, R.~Poncet and F.~Dias. \textit{The VOLNA code for the numerical modelling of tsunami waves: generation, propagation and inundation}. European Journal of Mechanics B/Fluids, \textbf{30}(6), 598--615, 2011 \\ % Arxiv
  \url{http://hal.archives-ouvertes.fr/hal-00454591/}
    
  \item \textbf{D.~Dutykh}, Th.~Katsaounis and D.~Mitsotakis. \textit{Finite volume schemes for dispersive wave propagation and runup}. J. Comp. Phys., \textbf{230}, 3035--3061, 2011 \\ % Arxiv
  \url{http://hal.archives-ouvertes.fr/hal-00472431/}
  
  %%% 2010: (4)
  \listpart{\centering\large\textbf{-- 2010 --}}
  
  \item Y.~Meyapin, \textbf{D.~Dutykh} and M.~Gisclon. \textit{Velocity and energy relaxation in two-phase flows}. Studies in Applied Mathematics, \textbf{125(2)}, 179 -- 212, 2010 \\ % Arxiv
  \url{http://hal.archives-ouvertes.fr/hal-00440852/}

  \item \textbf{D.~Dutykh} and D.~Mitsotakis. \textit{On the relevance of the dam break problem in the context of nonlinear shallow water equations}. Discrete and Continuous Dynamical Systems, \textbf{13}(4), 799--818, 2010 \\ % Arxiv
  \url{http://hal.archives-ouvertes.fr/hal-00369795/}
  
  \item \textbf{D.~Dutykh} and F.~Dias. \textit{Influence of sedimentary layering on tsunami generation}, Computer Methods in Applied Mechanics and Engineering, \textbf{199}, 1268--1275, 2010 \\ % Arxiv
  \url{http://hal.archives-ouvertes.fr/hal-00288696/}
  
  \item F.~Dias, \textbf{D.~Dutykh} and J.-M.~Ghidaglia. \textit{A two-fluid model for violent aerated flows}, Computers and Fluids, 39(2), 283--293, 2010 \\ % Arxiv
  \url{http://hal.archives-ouvertes.fr/hal-00285037/}
  
  %%% 2009: (4)
  \listpart{\centering\large\textbf{-- 2009 --}}
  
  \item \textbf{D.~Dutykh}. \textit{Group and phase velocities in the free-surface visco-potential flow: new kind of boundary layer induced instability}. Physics Letters A, \textbf{373}, 3212--3216, 2009 \\ % Arxiv
  \url{http://hal.archives-ouvertes.fr/hal-00334440/}
  
  \item \textbf{D.~Dutykh}. \textit{Visco-potential free-surface flows and long wave modelling}. European Journal of Mechanics B/Fluids, \textbf{28}(3), 430--443, 2009 \\ % Arxiv
  \url{http://hal.archives-ouvertes.fr/hal-00270926/}
  
  \item \textbf{D.~Dutykh} and F.~Dias. \textit{Energy of tsunami waves generated by bottom motion}. Proc. R. Soc. A (2009) \textbf{465}, 725--744 \\ % Arxiv
  \url{http://hal.archives-ouvertes.fr/hal-00311752/}
  
  \item \textbf{D.~Dutykh} and F.~Dias. \textit{Tsunami generation by dynamic displacement of sea bed due to dip-slip faulting}. Math. Comp. Sim., \textbf{80}(4), 837-848, 2009 \\ % Arxiv
  \url{http://hal.archives-ouvertes.fr/hal-00174439/}
  
  %%% 2008: (0)
  
  % Niente! Just a few proceedings.

  %%% 2007: (3)
  
  \listpart{\centering\large\textbf{-- 2007 --}}
  
  \item \textbf{D.~Dutykh} and F.~Dias. \textit{Viscous potential free-surface flows in a fluid layer of finite depth}, C. R. Acad. Sci. Paris, Ser. I, \textbf{345}, 113--118, 2007 \\ % Arxiv
  \url{http://hal.archives-ouvertes.fr/hal-00145315/}
  
  \item \textbf{D.~Dutykh} and F.~Dias. \textit{Dissipative Boussinesq equations}, C. R. Mcanique, \textbf{335}, 559--583, 2007 \\ % Arxiv
  \url{http://hal.archives-ouvertes.fr/hal-00137633/}
  
  \item  Y.~Kervella, \textbf{D.~Dutykh} and F.~Dias. \textit{Comparison between three-dimensional linear and nonlinear tsunami generation models}, Theor. Comput. Fluid Dyn., \textbf{21}:245--269, 2007 \\ % Arxiv
  \url{http://hal.archives-ouvertes.fr/hal-00113909/}
  
  %%% 2006: (1)
  
  \listpart{\centering\large\textbf{-- 2006 --}}
  
  \item \textbf{D.~Dutykh}, F.~Dias and Y.~Kervella. \textit{Linear theory of wave generation by a moving bottom}, C. R. Acad. Sci. Paris, Ser. I \textbf{343}, 499--504, 2006 \\ % Arxiv
  \url{http://hal.archives-ouvertes.fr/hal-00114954/}
 
\end{etaremune}

\separator
\subsubsection{Book chapters}

\begin{etaremune}

  %%% 2025 (1)

  \listpart{\centering\large\textbf{-- 2025 --}}

  \item R.~Matar, N.~Abcha, N.~Lecoq, E.-I.~Turki, I.~Abroug and \textbf{D.~Dutykh}. \textit{Exploring Extreme Wave Propagation in Coastal Zones: A Combined Physical and Numerical Modeling Study}, In A.-C.~Bennis, J.-C.~Dauvin, E.~Feunteun, T.~Komatsu, O.~Matsuda and P.~Prouzet (Eds.) Constraints and Adaptations to Global Change at the Land-Sea Interface: For a Shared Ecological and Energy Transition, Proceedings of the 19\up{th} French--Japanese Oceanography Symposium, COAST 2023, Springer, Cham, pp.~3--18, 2025 % No (HAL & Arxiv)
  
  %%% 2024 (1)

  \listpart{\centering\large\textbf{-- 2024 --}}

  \item M.~Zafar, \textbf{D.~Dutykh}, P.~Sabatier, M.~Banjan and J.~Kim. \textit{Uncovering a Paleotsunami Triggered by Mass-Movement in an Alpine Lake}. In: P.~Gourbesville, G.~Caignaert (Eds.) Advances in Hydroinformatics --- SimHydro 2023 Volume 2. SimHydro 2023. Springer Water. Springer, Singapore, pp.~47--64, 2024 \\ % Yes (HAL, Arxiv, RG)
  \url{https://hal.science/hal-04261487/}

  %%% 2022 (1)

  \listpart{\centering\large\textbf{-- 2022 --}}
  
  \item T.S.B.~Abd~Manan, T.~Khan, W.H.M.~Wan~Mohtar, A.~Machmudah, \textbf{D.~Dutykh}, S.~Qazi, A.~Ahmad and N.~Wan~Rasdi. \textit{Bioremediation of wastewater using algae for potential renewable bioenergy cogeneration}, In A.~Ahmad, F.~Banat and H.~Taher (Eds.) Algal Biotechnology: Integrated Algal Engineering for Bioenergy, Bioremediation, and Biomedical Applications, Elsevier, Amsterdam, pp.~47--62, 2022 % No (HAL & Arxiv)

  %%% 2021 (1)

  \listpart{\centering\large\textbf{-- 2021 --}}
  
  \item V.~Roubtsov and \textbf{D.~Dutykh}. \textit{Poisson and Symplectic structures, Hamiltonian action, momentum and reduction}, In M.~Ulan and E.~Schneider (Eds.) Differential Geometry, Differential Equations, and Mathematical Physics. Birkh\"auser, Cham, pp.~1--29, 2021 \\ % Arxiv
  \url{https://hal.archives-ouvertes.fr/hal-02522156/}

  %%% 2019 (1)

  \listpart{\centering\large\textbf{-- 2019 --}}

  \item T.~Torsvik, A.~Abdalazeez, \textbf{D.~Dutykh}, P.~Denissenko and I.~Didenkulova. \textit{Dispersive and non-dispersive nonlinear long wave transformations: numerical and experimental results}, In A.~\textsc{Berezovski} and T.~\textsc{Soomere} (Eds.) Applied Wave Mathematics II, Mathematics of Planet Earth, Vol.~\textbf{6}. pp.~41--66, Springer Cham, 2019 \\ % Arxiv
  \url{https://hal.archives-ouvertes.fr/hal-02289778/}
  
  %%% 2018 (1)

  \listpart{\centering\large\textbf{-- 2018 --}}

  \item A.~Dur\'an, \textbf{D.~Dutykh} and D.~Mitsotakis. \textit{Peregrine's system revisited}, In N.~\textsc{Abcha}, E.~\textsc{Pelinovsky} and I.~\textsc{Mutabazi} (Eds.) Nonlinear Waves and Pattern Dynamics, pp.~3--43, Springer Cham, 2018 \\ % Arxiv
  \url{https://hal.archives-ouvertes.fr/hal-01703491/}
  
  %%% 2016 (1)

  \listpart{\centering\large\textbf{-- 2016 --}}

  \item D.~Clamond and \textbf{D.~Dutykh}. \textit{Modeling water waves beyond perturbations}, in E.~\textsc{Tobisch} (Ed.): New Approaches to Nonlinear Waves, Lecture Notes in Physics (\textbf{908}), 197--210, Springer, 2016 \\ % Arxiv
  \url{https://hal.archives-ouvertes.fr/hal-01102120/}
  
  %%% 2014 (2)

  \listpart{\centering\large\textbf{-- 2014 --}}

  \item D.~Clamond and \textbf{D.~Dutykh}. \textit{A Non-Hydrostatic Non-Dispersive Shallow Water Model}, Ph.~\textsc{Goubersville} \emph{et al.} (Eds.): Springer Hydrogeology. Advances in Hydroinformatics: SIMHYDRO 2012 --- New Frontiers of Simulation, 197--206, Springer Singapore 2014 \\ % No (Arxiv)
  \url{https://hal.archives-ouvertes.fr/hal-00907110/}

  \item V.~Guinot, D.~Clamond and \textbf{D.~Dutykh}. \textit{Finite Volume Implementation of Non-Dispersive, Non-Hydrostatic Shallow Water Equations}, Ph.~\textsc{Goubersville} \emph{et al.} (Eds.): Springer Hydrogeology. Advances in Hydroinformatics: SIMHYDRO 2012 --- New Frontiers of Simulation, 189--196, Springer Singapore 2014 \\ % No (Arxiv)
  \url{https://hal.archives-ouvertes.fr/hal-00907108/}
  
  %%% 2011 (1)

  \listpart{\centering\large\textbf{-- 2011 --}}

  \item Y.~Meyapin, \textbf{D.~Dutykh} and M.~Gisclon. \textit{Two-fluid barotropic models for powder-snow avalanche flows}, E. Krause \emph{et al.} (Eds.): Computational Sci. \& High Performance Computing IV, NNFM 115, pp. 219--232. Springer-Verlag Berlin Heidelberg 2011 \\ % Arxiv
  \url{http://hal.archives-ouvertes.fr/hal-00394437/}
  
  %%% 2007 (1)

  \listpart{\centering\large\textbf{-- 2007 --}}
  
  \item \textbf{D.~Dutykh} and F.~Dias, \textit{Water waves generated by a moving bottom}. In book: ``Tsunami and Nonlinear Waves'', A.~\textsc{Kundu} (Editor), pp. 65--95, Springer Verlag 2007, Approx. 325 p., 170 illus., Hardcover, ISBN: 978-3-540-71255-8 \\ % Arxiv
  \url{http://hal.archives-ouvertes.fr/hal-00115875/}
  
  %%% 2006 (1)

  \listpart{\centering\large\textbf{-- 2006 --}}
  
  \item F.~Dias and \textbf{D.~Dutykh}. \textit{Dynamics of tsunami waves}. In Book: ``Extreme Man-Made and Natural Hazards in Dynamics of Structures'', A.~\textsc{Ibrahimbegovic} and I.~\textsc{Kozar} (Eds), Springer Dordrecht, NATO Advanced Research Workshop, Opatija, Croatia, May 28 --- June 1, pp. 35--60, 2006 \\ % Arxiv
  \url{http://hal.archives-ouvertes.fr/hal-00113612/}
  
\end{etaremune}

\separator
\subsubsection{Peer-reviewed conference proceedings}

\begin{etaremune}

  %%% 2022 (1)

  \listpart{\centering\large\textbf{-- 2022 --}}

  \item S.~Mustatea, M.~Aupetit, J.~Peltonen, S.~Lespinats, \textbf{D.~Dutykh}. \textit{Supervised dimensionality reduction technique accounting for soft classes}, European Symposium on Artificial Neural Networks, Computational Intelligence and Machine Learning (ESANN), Bruges, Belgium, 5--7 October 2022 \\ % No (HAL & Arxiv) Yes (RG)
  \url{https://www.esann.org/sites/default/files/proceedings/2022/ES2022-26.pdf}

  %%% 2020 (3)

  \listpart{\centering\large\textbf{-- 2020 --}}
  
  \item B.~Colange, J.~Peltonen, M.~Aupetit, \textbf{D.~Dutykh} and S.~Lespinats. \textit{Steering Distortions to Preserve Classes and Neighbors in Supervised Dimensionality Reduction}, $34$\up{th} Conference on Neural Information Processing Systems (NeurIPS 2020), Vancouver, Canada, 2020 \\ % No (HAL & Arxiv) NeurIPS2020
  {\small \url{https://proceedings.neurips.cc/paper/2020/hash/99607461cdb9c26e2bd5f31b12dcf27a-Abstract.html}}
  
  \item M.~Loukili, K.~Kotrasova and D.~\textbf{Dutykh}. \textit{A computational simulation of steady natural convection in an $H-$form cavity}. In Silhavy R., Silhavy P., Prokopova Z. (Eds.) Software Engineering Perspectives in Intelligent Systems. CoMeSySo 2020. Advances in Intelligent Systems and Computing, Vol. \textbf{1295}, pp.~164-177, Springer International Publishing, Cham, 2020 \\ % Arxiv
  \url{https://hal.archives-ouvertes.fr/hal-02615655/}

  \item A.~Abdalazeez, I.~Didenkulova and \textbf{D.~Dutykh}. \textit{Dispersive effects during long wave run-up on a plane beach} in ``Advances in Natural Hazards and Hydrological Risks: Meeting the Challenge'', Proceedings of the 2\up{nd} International Workshop on Natural Hazards (NatHaz'19), Pico Island -- the Azores 2019, F.~Fernandes, A.~Malheiro, H.I.~Chamin\'e (Eds.), pp.~143--146, Springer International Publishing, Cham, 2020 \\ % Arxiv
  \url{https://hal.archives-ouvertes.fr/hal-02366937/}
  
  %%% 2019 (3)

  \listpart{\centering\large\textbf{-- 2019 --}}

  \item B.~Colange, L.~Vuillon, S.~Lespinats and \textbf{D.~Dutykh}. \textit{Interpreting Distortions in Dimensionality Reduction by Superimposing Neighbourhood Graphs}. 2019 IEEE Visualization Conference (VIS), 20 -- 25 October, Vancouver, BC, Canada, 2019 \\ % Arxiv
  \url{https://hal.archives-ouvertes.fr/hal-02290875/}

  \item M.~Abdykarim, J.~Berger, \textbf{D.~Dutykh} and A.~Agbossou. \textit{An efficient numerical method for a long term simulation of heat and mass transfer: the case of an insulated rammed earth wall}. V.~Corrado, E.~Fabrizio, A.~Gasparella and F.~Patuzzi (Eds.), Proceedings of the $16$\up{th} IBPSA Conference, pp. 1444 -- 1451, Rome, Italy, September 2 -- 4, 2019, ISBN: $978-1-7750520-1-2$ \\ % Arxiv
  \url{https://hal.archives-ouvertes.fr/hal-02288858/}

  \item H.~Geoffroy, J.~Berger, B.~Colange, S.~Lespinats, \textbf{D.~Dutykh}, C.~Buh\'e and G.~Sauce. \textit{Use of Multidimensional Scaling for Fault Detection or Monitoring Support in A Continuous Commissioning}. V.~Corrado, E.~Fabrizio, A.~Gasparella and F.~Patuzzi (Eds.), Proceedings of the $16$\up{th} IBPSA Conference, pp. 877 -- 884, Rome, Italy, September 2 -- 4, 2019, ISBN: $978-1-7750520-1-2$ \\ % No (Arxiv)
  \url{https://hal.archives-ouvertes.fr/hal-02411240/}

  %%% 2012 (2)

  \listpart{\centering\large\textbf{-- 2012 --}}

  \item T.~Stefanakis, F.~Dias and \textbf{D.~Dutykh}. \textit{Resonant long-wave run-up on a plane beach}. ISOPE-2012 Rhodes Conference Proceedings, 2012 \\ % No (Arxiv)
  \url{http://hal.archives-ouvertes.fr/hal-00728747/}

  \item L.~O'Brien, P.~Christodoulides, E.~Renzi, \textbf{D.~Dutykh} and F.~Dias. \textit{The force of a tsunami on a wave energy converter}. ISOPE-2012 Rhodes Conference Proceedings, 2012 \\ % Arxiv
  \url{http://hal.archives-ouvertes.fr/hal-00728888/}
  
  %%% 2011 (2)

  \listpart{\centering\large\textbf{-- 2011 --}}

  \item \textbf{D.~Dutykh}, D.~Mitsotakis, S.~Beisel and N.~Shokina. \textit{Dispersive waves generated by an underwater landslide}. Numerical methods for Hyperbolic Equations. Eds: Vazquez-Cendon \emph{et al.}, Taylor \& Francis Group, London, pp. 245--250, 2013. Proceedings of the Numerical Methods for Hyperbolic Equations: Theory and Applications. International Conference to honour Professor E.F. Toro in the month of his 65th birthday. Santiago de Compostela, Spain, July 4 -- 8, 2011 \\ % Arxiv
  \url{http://hal.archives-ouvertes.fr/hal-00637102/}

  \item \textbf{D.~Dutykh}, Th.~Katsaounis and D.~Mitsotakis. \textit{Dispersive wave runup on non-uniform shores}. In: Fort J., F\"urst J., Halama J., Herbin R., Hubert F. (Eds.) Finite Volumes For Complex Applications VI --- Problems \& Perspectives. Springer Proceedings in Mathematics, 2011, Volume \textbf{4}, Part 1, pp. 389--397 \\ % Arxiv
  \url{http://hal.archives-ouvertes.fr/hal-00553762/}
  
  %%% 2009 (1)

  \listpart{\centering\large\textbf{-- 2009 --}}

  \item \textbf{D.~Dutykh} and F.~Dias. \textit{How does sedimentary layering affect the generation of tsunamis?} Proceedings of OMAE 2009, 28th International Conference on Ocean, Offshore and Arctic Engineering, May 31 -- June 5, 2009, Honolulu, USA % No (HAL & Arxiv)
  
  %%% 2008 (2)

  \listpart{\centering\large\textbf{-- 2008 --}}

  \item \textbf{D.~Dutykh}. \textit{Visco potential free-surface flows}, XXII ICTAM, 25 -- 29 August 2008, Adelaide, Australia % No (HAL & Axiv)
  
  \item F.~Dias, \textbf{D.~Dutykh} and J.-M.~Ghidaglia. \textit{Simulation of Free Surface Compressible Flows Via a Two Fluid Model}, OMAE 2008, Nick~\textsc{Newman}'s Symposium on Marine Hydrodynamics, \textbf{6}, 43--50, 2008. Estoril, Portugal, 15 -- 20 June 2008 \\ % Arxiv
  \url{http://hal.archives-ouvertes.fr/hal-00258161/}
  
\end{etaremune}

\separator
\subsubsection{Conference proceedings}

\begin{etaremune}

  %%% 2025 (2)

  \listpart{\centering\large\textbf{-- 2025 --}}

  \item S.~Mukherjee, L.~Vuillon, L.~Bou-Nassif, S.~Giroux-Julien, H.~Pabiou, \textbf{D.~Dutykh} and I.~Tsanakas. \textit{Temporal Graph Neural Networks for Early Anomaly Detection and Performance Prediction via PV System Monitoring Data} in Proc. 42nd European Photovoltaic Solar Energy Conference and Exhibition (EU PVSEC 2025), Bilbao, Spain, 020338, pp.~001--003, 2025 \\ % Yes (HAL, Arxiv, RG)
  \url{https://arxiv.org/abs/2512.03114/}

  \item M.~Zafar, P.~Sabatier, \textbf{D.~Dutykh}, H.~Jomard, W.~Rapuc, P.~Lajeunesse and E.~Chapron. \textit{Modeling earthquake-induced seiche process and subsequent homogenite deposits in lacustrine setting}, EGU General Assembly 2025, Vienna, Austria, 27 Apr -- 2 May 2025, EGU25-2461, 2025 \\ % No (HAL, Arxiv, RG)
  \url{https://doi.org/10.5194/egusphere-egu25-2461/}
  
  %%% 2024 (6)

  \listpart{\centering\large\textbf{-- 2024 --}}

  \item A.~Rashidi, \textbf{D.~Dutykh}, Ch.~Beck and M.~Najaftomaraei. \textit{Unraveling Tsunami Hazards along the Lesser Antilles, Eastern Caribbean Plate}, Proceedings of the 21st Iranian Geophysical Conference, December 10-11, Tehran, Iran, pp.~1318--1323, 2024 % Yes - RG, No - (HAL, Arxiv)

  \item S.~Mukherjee, L.~Vuillon, \textbf{D.~Dutykh} and I.~Tsanakas. \textit{Dimensionality Reduction of Environmental Data for Long-Term PV Performance Analysis Using Graph Based Methods}, EU PVSEC 2024, \textbf{020411}, pp.~001--004, 2024 \\
  \url{https://userarea.eupvsec.org/proceedings/EU-PVSEC-2024/4CV.1.27/}

  \item C.~C\'ardenas-Bravo, S.~Lespinats and \textbf{D.~Dutykh}. \textit{A Practical Example of the Impact of Uncertainty on the One-Dimensional Single-Diode Model}, 2024 IEEE International Symposium on Systems Engineering (ISSE), Perugia, Italy, pp.~1--5, 2024 \\
  \url{https://ieeexplore.ieee.org/document/10741111/}

  \item M.~Zafar, \textbf{D.~Dutykh}, P.~Sabatier, M.~Banjan and J.~Kim. \textit{Uncovering a Paleotsunami Triggered by Mass-Movement in an Alpine Lake}. In: P.~Gourbesville, G.~Caignaert (Eds.) Advances in Hydroinformatics --- SimHydro 2023 Volume 2. SimHydro 2023. Springer Water. Springer, Singapore, pp.~47--64, 2024 \\ % Yes (HAL, Arxiv, RG)
  \url{https://hal.science/hal-04261487/}

  \item A.~Rashidi, M.~Mokhtari, \textbf{D.~Dutykh}, M.~Masoodi, P.~Faridi and S.~Kiani. \textit{A glimpse into tsunami hazard research in Makran with a focus on complex tsunamis}. The 9\up{th} International Conference on Seismology and Earthquake Engineering, Tehran, Iran, 2024 % Yes - RG, No - (HAL, Arxiv)

  \item F.~Carbone and \textbf{D.~Dutykh}. \textit{Route to chaos and resonant triads interaction in a truncated Rotating Nonlinear shallow-water model}, EGU General Assembly 2024, Vienna, Austria, 14--19 Apr 2024, EGU24--13180, 2024 \\ % Yes - RG, No - (HAL & Arxiv)
  \url{https://doi.org/10.5194/egusphere-egu24-13180/}

  %%% 2023 (1)

  \listpart{\centering\large\textbf{-- 2023 --}}

  \item M.~Bowen, P.~Samozino, M.~Vonderscher, \textbf{D.~Dutykh} and B.~Morel. \textit{Development of a force-endurance model able to describe the muscle fatigability in the severe domain and validation of the RACLET test}, 28\up{th} annual congress of the European College of Sport Science, Paris, France, 4--7 July 2023 \\ % Yes - (HAL & RG), No - (Arxiv)
  \url{https://hal.science/hal-04084767/}

  %%% 2022 (3)

  \listpart{\centering\large\textbf{-- 2022 --}}

  \item C.~Cardenas-Bravo, \textbf{D.~Dutykh} and D.L.~Ha. \textit{Computation of Faulty IV Curves Based on a Distributed Solar Cell Algorithm}, 8\up{th} World Conference on Photovoltaic Energy Conversion, Milano, Italy, 26--30 September 2022, pp.~701--703 \\ % No (HAL & Arxiv), Yes (RG)
  \url{https://www.eupvsec-proceedings.com/proceedings?char=C&paper=50890}
  
  \item M.~Cugnet, F.~Gallois, A.~Kirchev and \textbf{D.~Dutykh}. \textit{Understanding self-discharge or what's going on inside a lead-acid battery when nothing happens outside}, AABC Europe --- 12\up{th} International Advanced Automotive Battery Conference, 13 -- 15 June 2022, Mainz, Germany \\
  \url{https://hal.insa-toulouse.fr/LITEN/cea-03715092/}
  
  \item I.~Didenkulova, A.~Abdalazeez, \textbf{D.~Dutykh} and P.~Denissenko. \textit{Effects of coastal roughness on long wave runup}, EGU General Assembly 2022, Vienna, Austria, 23 -- 27 May 2022, EGU22-8520 \\
  \url{https://doi.org/10.5194/egusphere-egu22-8520/}

  %%% 2020 (2)

  \listpart{\centering\large\textbf{-- 2020 --}}
  
  \item A.~Rashidi, \textbf{D.~Dutykh}, Z.H.~Shomali and N.K.~Farajkhah. \textit{Probabilistic Tsunami Hazard of Splay and Normal Faults in the Western Makran/Iran}, The Second Eurasian RISK-2020 Conference and Symposium, Tbilisi, Georgia \\ % RG
  \url{https://www.researchgate.net/publication/343336669_Probabilistic_Tsunami_Hazard_of_Splay_and_Normal_Faults_in_the_Western_MakranIran/}
  
  \item S.~Rusconi, \textbf{D.~Dutykh}, A.~Zarnescu, D.~Sokolovski and E.~Akhmatskaya. \textit{Population balance approach for predicting polymer particles morphology}. The 11\up{th} Conference on Dynamical Systems Applied to Biology and Natural Sciences (DSABNS), Trento, Italy, 4 -- 7 February 2020. ISBN: $978-989-98750-7-4$ \\ % No (Arxiv)
  \url{https://hal.archives-ouvertes.fr/hal-02518323/}

  %%% 2019 (1)

  \listpart{\centering\large\textbf{-- 2019 --}}

  \item A.~Abdalazeez, I.~Didenkulova and \textbf{D.~Dutykh}. \textit{Nonlinear deformation and run-up of tsunami waves of positive polarity: numerical simulations and analytical predictions}. The First Eurasian conference ``Risk -- 2019'', Baku, Azerbaijan; 22 -- 24 May 2019 \\ % No (not a problem)
  \url{https://hal.archives-ouvertes.fr/hal-02145105/}
  
  %%% 2017 (3)

  \listpart{\centering\large\textbf{-- 2017 --}}

  \item I.~Didenkulova, D.~Senichev and \textbf{D.~Dutykh}. \textit{Statistics for long irregular wave run-up on a plane beach from direct numerical simulations}. European Geosciences Union, Vienna, Austria; 23 -- 28 April 2017. Geophysical Research Abstracts, \textbf{19}, p.~19133 \\ % Yes - RG, No - (Arxiv & HAL)
  \url{https://meetingorganizer.copernicus.org/EGU2017/EGU2017-19133.pdf}
  
  \item D.~Senichev, I.~Didenkulova and \textbf{D.~Dutykh}. \textit{Study of statistics of random wave runup on a beach using direct numerical simulations}. Proceedings of the 23\up{rd} International scientific conference ``Information Systems and Technologies'' (IST--2017), 21\up{st} April 2017, Nizhny Novgorod, Russia; pp.~1001--1006 (in Russian) % Yes - RG, No - (Arxiv & HAL)
  
  \item M.~Gisclon, M.~Chhay, \textbf{D.~Dutykh} and C.~Ruyer-Quil. \textit{Mod\'elisation math\'ematique des films minces avec applications aux transferts de chaleur}. Congr\`es Fran\c{c}ais de M\'ecanique, Lille, France; 28 August -- 1 September 2017. Publisher: Association Fran\c{c}aise de M\'ecanique (AFM) \\ % Yes - RG, No - (HAL & Arxiv)
  \url{https://cfm2017.sciencesconf.org/135353/template_cfm2017_vf.pdf}
  
  %%% 2016 (1)

  \listpart{\centering\large\textbf{-- 2016 --}}
  
  \item I.~Didenkulova, \textbf{D.~Dutykh} and D.~Senichev. \textit{Statistics for long wave run-up on a slopping beach: theoretical predictions and experimental data}. 15\up{th} Plinius Conference on Mediterranean Risks, Giardini Naxos, Italy; 8--11 June 2016. Publisher: Plinius Conference Abstracts, \textbf{15}, p.~38. % Yes - RG, No - (HAL & Arxiv)

  %%% !!! RG Start Here and Go Above %%%
  
  %%% 2015 (2)

  \listpart{\centering\large\textbf{-- 2015 --}}
  
  \item M.~Chhay, \textbf{D.~Dutykh}, M.~Gisclon and C.~Ruyer-Quil. \textit{Mod\'elisation math\'ematiques des films minces}. Congr\`es Fran\c{c}ais de M\'ecanique, Lyon, France; 24 -- 28 August 2015. Publisher: Association Fran\c{c}aise de M\'ecanique (AFM) \\ % Yes - RG, No - (HAL & Arxiv)
  
  \item D.~Clamond, \textbf{D.~Dutykh} and A.~Galligo. \textit{Computer Algebra Applied to a Solitary Waves Study}. In Proceedings of the 2015 ACM on International Symposium on Symbolic and Algebraic Computation -- ISSAC'15, ACM Press, 125--132, 2015 % Yes - RG, No - (HAL & Arxiv)
  
  %%% 2014 (4)

  \listpart{\centering\large\textbf{-- 2014 --}}
  
  \item A.~Galligo, \textbf{D.~Dutykh} and D.~Clamond. \textit{On detection of solitary waves, using phase diagrams and real discriminant}. In J.E.~Garcia, J.~Fern\'andez S\'anchez and M.~Sombra (Eds.), Proceedings of the Encuentros de Algebra Computacional y aplicaciones Conference, Barcelona, Spain, 18 -- 20 June 2014, pp. 119--122 % Yes - RG, No - (HAL & Arxiv)
  
  \item \textbf{D.~Dutykh} and J.-G.~Caputo. \textit{Sine-Gordon dynamics on graphs}. In O.O.~Kochubey \emph{et al}. (Eds.), Applied problems of the fluid mechanics and heat and mass transfer (pp. 29--31). Dnipropetrovsk, Ukraine. Dnipropetrovsk National University. pp 192, 2014 % Yes - RG, No - (HAL & Arxiv)
  
  \item \textbf{D.~Dutykh} and D.~Clamond. \textit{Modified Shallow Water Equations for Mild-slope Seabeds}. IWWWFB29, 30 March -- 2 April 2014, Osaka, Japan, IWWWFB, 2014 % Yes - RG, No - (HAL & Arxiv)
  
  \item F.~Carbone, \textbf{D.~Dutykh}, J.M.~Dudley and F.~Dias. \textit{Extreme wave run-up on a vertical cliff}. In Zbornik radova konferencije MIT 2013, pp. 99--103, Beograd, Serbia, 2014 % Yes - RG, No - (HAL & Arxiv)
  
  %%% 2013 (1)

  \listpart{\centering\large\textbf{-- 2013 --}}
  
  \item F.~Carbone, \textbf{D.~Dutykh}, J.M.~Dudley and F.~Dias. \textit{Extreme wave run-up on a vertical cliff}. IWWWFB28, 7 -- 10 April 2013, Marseille, France \\ % Yes - (HAL & RG), No - (Arxiv)
  \url{https://hal.archives-ouvertes.fr/hal-00927313/}
  
  %%% 2012 (1)

  \listpart{\centering\large\textbf{-- 2012 --}}
  
  \item \textbf{D.~Dutykh}, D.~Mitsotakis, S.~Beisel and N.~Shokina. \textit{On waves generated by an underwater landslide}. In Proceedings of the IV Conference ``Applied Problems of the fluid mechanics, heat and mass transfer'', 1 -- 3 November 2012, Dnepropetrovsk, Ukraine, pp. 75--79, 2012 % Yes - RG, No - (HAL & Arxiv)
  
  %%% 2010 (2)

  \listpart{\centering\large\textbf{-- 2010 --}}
  
  \item \textbf{D.~Dutykh}, Th.~Katsaounis and D.~Mitsotakis. \textit{Finite volume schemes for Boussinesq type equations}. Proceedings of Colloque EDP-Normandie, 28 -- 29 October 2010, Caen, France, pp. 15--21 \\ % Yes - (Arxiv & HAL & RG)
  \url{http://hal.archives-ouvertes.fr/hal-00553754/}

  \item D.~Clamond and \textbf{D.~Dutykh}. \textit{Dispersive wave equation derivation from a relaxed variational formulation}. Applied problems of aerodynamics, heat and mass transfers, pp. 40--42, Dnepropetrovsk, Ukraine, November 4 -- 6, 2010 % Yes - RG, No - (HAL & Arxiv)
  
  %%% 2008 (1)

  \listpart{\centering\large\textbf{-- 2008 --}}

  \item \textbf{D.~Dutykh} and F.~Dias. \textit{Tsunami wave energy}, 4th Canadian Conference on Geohazards, Universit Laval, May 20 -- 24, 7 p., 2008 \\ % Yes - RG & HAL, No - Arxiv
  \url{https://hal.science/hal-04474849/}
  
  %%% 2007 (2)

  \listpart{\centering\large\textbf{-- 2007 --}}

  \item \textbf{D.~Dutykh} and F.~Dias, \textit{Fault dynamics and tsunami generation}, ECCOMAS Thematic Conference on Multi-scale Computational Methods for Solids and Fluids. A.~Ibrahimbegovic, F.~Dias, H.~Matthies, P.~Wriggers (eds.), 79--81, 2007 % No - (HAL & Arxiv & RG)

  \item C.~Kassiotis, F.~Dias, A.~Ibrahimbegovic and \textbf{D.~Dutykh}, \textit{A partitioned approach to model tsunami impact on coastal protections}, ECCOMAS Thematic Conference on Multi-scale Computational Methods for Solids and Fluids. A.~Ibrahimbegovic, F.~Dias, H.~Matthies, P.~Wriggers (eds.), 134--139, 2007 % Yes - RG, No - (HAL & Arxiv)
  
\end{etaremune}

\separator
\subsubsection{Research reports}

\begin{etaremune}

  %%% 2020 (1)

  \listpart{\centering\large\textbf{-- 2020 --}}
  
  \item J.~Berger, T.~Busser, \textbf{D.~Dutykh} and N.~Mendes. Retraction notice to ``\textit{On the estimation of moisture permeability and advection coefficients of a wood fibre material using the optimal experiment design approach}'' [Exp. Therm. Fluid Sci. 90 (2017) 246--259], Exp. Therm. Fluid Sci., \textbf{113}, 109808, 2020 % No (HAL & Arxiv & RG)

  %%% 2016 (1)

  \listpart{\centering\large\textbf{-- 2016 --}}

  \item \textbf{D.~Dutykh}. \textit{How to overcome the Courant-Friedrichs-Lewy condition of explicit discretizations?}. Technical report, 20 pp, 2016 \\ % HAL & Arxix & RG
  \url{https://hal.archives-ouvertes.fr/hal-01401125/}
  
  %%% 2015 (1)

  \listpart{\centering\large\textbf{-- 2015 --}}

  \item \textbf{D.~Dutykh} and L.~Gosse. \textit{Some topics of the NumHyp--2015' discussion session}. 25 pp., 2015 \\ % Yes - HAL & RG, No - Arxiv
  \url{https://hal.archives-ouvertes.fr/hal-02485301/}
  
  %%% 2014 (1)

  \listpart{\centering\large\textbf{-- 2014 --}}
  
  \item Ch.~Lalanne, A.~Rafiee, \textbf{D.~Dutykh}, M.~Lysaght and F.~Dias. \textit{Enabling the UCD--SPH code on the Xeon Phi}, 12 pp., 2014 \\ % Yes - HAL & RG, No - Arxiv
  \url{http://hal.archives-ouvertes.fr/hal-00927227/}
  
  %%% 2011 (1)

  \listpart{\centering\large\textbf{-- 2011 --}}

  \item F.~Fedele and \textbf{D.~Dutykh}. \textit{Hamiltonian description and traveling waves of the spatial Dysthe equations}, 2011 \\ % Arxiv & HAL & RG
  \url{http://hal.archives-ouvertes.fr/hal-00632862/}
  
  %%% 2009 (1)

  \listpart{\centering\large\textbf{-- 2009 --}}
  
  \item F.~Dias, \textbf{D.~Dutykh} and J.-M.~Ghidaglia. \textit{A compressible two-fluid model for the finite volume simulation of violent aerated flows. Analytical properties and numerical results}, 2009 \\ % Arxiv & HAL & RG
  \url{http://hal.archives-ouvertes.fr/hal-00279671/}
  
  %%% 2008 (1)

  \listpart{\centering\large\textbf{-- 2008 --}}
  
  \item \textbf{D.~Dutykh}. \textit{Visco-potential free-surface flows}. Research report of CMLA, 2008 % Yes - RG, No - (HAL & Arxiv) - No Need to upload to Arxiv since very close to the published paper
  
\end{etaremune}

\separator
\subsubsection{Book reviews}

\begin{etaremune}

  \item M. S.~Howe, \textit{Hydrodynamics and Sound}, Cambridge University Press, Cambridge (2007). European Journal of Mechanics - B/Fluids, \textbf{27(2)}, 218, 2008 \\ % Yes - RG & HAL, No - Arxiv (not in the format)
  \url{https://hal.science/hal-04474814/}
  
\end{etaremune}

\separator
\subsubsection{Theses}

\begin{etaremune}
  
  \item \textbf{D.~Dutykh}. \textit{Mathematical modeling in the environment}, Habilitation \`a diriger des recherches, University of Savoie, 2010 \\ % Yes - (TEL & RG), No (Arxiv)
  \url{http://tel.archives-ouvertes.fr/tel-00542937/}
  
  \item \textbf{D.~Dutykh}. \textit{Mathematical modeling of tsunami waves}, PhD thesis, CMLA, ENS de Cachan, 2007 \\ % Yes - (TEL & RG), No - (Arxiv)
  \url{http://tel.archives-ouvertes.fr/tel-00194763/}
  
  \item \textbf{D.~Dutykh}. \textit{Moving load on a layered floating ice sheet}, Master 2 MN2MC thesis, CMLA, ENS de Cachan, 2005 \\ % Yes - RG, HAL & Arxiv
  \url{https://arxiv.org/abs/2402.16890/}
  
  \item \textbf{D.~Dutykh}. \textit{Harmonic oscillations of an inhomogeneous elastic layer under the action of a stamp} (in Ukrainian), Master thesis, Faculty of Applied Mathematics, Oles Honchar National University, Dnepropetrovsk, Ukraine, 2004 % Yes - RG, No - (HAL & Arxiv)

  \item \textbf{D.~Dutykh}. \textit{Harmonic oscillations of an inhomogeneous elastic layer} (in Ukrainian), Bachelor thesis, Faculty of Applied Mathematics, Oles Honchar National University, Dnepropetrovsk, Ukraine, 2003 % Yes - RG, No - (HAL & Arxiv)
  
\end{etaremune}

\separator
\subsubsection{Various writings}

\begin{etaremune}

  \item \textbf{D.~Dutykh}. \textit{How to overcome the Courant-Friedrichs-Lewy condition of explicit discretizations?}. Technical report, 20 pp, 2016 \\ % Yes - Arxiv & HAL & RG
  \url{https://hal.archives-ouvertes.fr/hal-01401125/}
  
  \item \textbf{D.~Dutykh}. \textit{A brief introduction to pseudo-spectral methods: application to diffusion problems}. Lecture notes, 38 pp, 2016 \\ % Yes - Arxiv & CEL & RG
  \url{https://cel.archives-ouvertes.fr/cel-01256472/}
  
  \item \textbf{D.~Dutykh}. \textit{Introduction into Hydrodynamics. Variational point of view}. Lecture notes (work in progress), 142 pp, 2015 \\ % No (HAL & Arxiv)
  \url{https://github.com/dutykh/hydro/}
  
  \item \textbf{D.~Dutykh}. \textit{My favourite books, papers and software libraries}. Informal notes (work in progress), 18 pp, 2015 \\ % No (HAL & Arxiv & RG)
  \url{https://github.com/dutykh/libs/}
  
  \item \textbf{D.~Dutykh}. \textit{Mathematical exercises (with solutions)}. Work in progress, 40 pp, 2015 \\ % No (HAL & Arxiv & RG)
  \url{https://github.com/dutykh/exos/}
  
\end{etaremune}

\separator
\subsubsection{General audience articles}

\begin{etaremune}

  \item \href{https://www.univ-smb.fr/2020/12/09/classnerv-une-nouvelle-methode-extremement-efficace-pour-lanalyse-de-donnees/}{ClassNeRV, une nouvelle m\'ethode extr\^emement efficace pour l'analyse de donn\'ees}, Le Fil d'Actualit\'e de l'Universit\'e Savoie Mont Blanc, December 9, 2020

  \item \href{http://www.scrivial.com/articles/a-dive-into-tsunami-the-terrifying-energy-it-possesses}{A dive into tsunami --- the terrifying energy it possesses!} \href{http://www.scrivial.com/}{Scrivial.com}, 2015
  
  \item C.~Acary-Robert, D.~Bresch and \textbf{D.~Dutykh}. \textit{Simulation d'avalanches de neige}. Actualit\'es scientifiques de l'INSMI (CNRS), 14 mars 2012 \\
  \url{http://www.cnrs.fr/insmi/spip.php?article441}
  
  \item C.~Acary-Robert, \textbf{D.~Dutykh} and M.~Gisclon. \textit{Un modello per simulare numericamente le valanghe di neve}. Translation by Roberto Natalini, 2011 \\
  {\small\url{maddmaths.simai.eu/focus/un-modello-per-simulare-numericamente-le-valanghe-di-neve/}}

  \item C.~Acary-Robert, \textbf{D.~Dutykh} and M.~Gisclon. \textit{Une approche pour simuler des avalanches de neige}. \href{http://images.math.cnrs.fr/}{Images des math\'ematiques}, 28 d\'ecembre 2011 \\
  \url{http://images.math.cnrs.fr/Une-approche-pour-simuler-des.html}
  
  \item \href{https://www.lemonde.fr/planete/article/2011/09/29/tsunamis-gare-aux-avalanches-et-a-la-deuxieme-vague_1580151_3244.html}{\textit{Tsunamis: gare aux ``avalanches'' et \`a la deuxi\`eme vague}}. Le Monde, 1\up{er} Octobre 2011

  \item \textit{New research may explain high runup from tsunami waves}. \href{http://physicsbuzz.physicscentral.com/2011/09/new-research-may-explain-high-runup.html}{PhysicsCentral}, Blog of the American Physical Society. September, 19, 2011

  \item \textit{Tsunami Puzzle Explained}. Physical Review Focus, 16 September 2011 \\
  \url{http://focus.aps.org/story/v28/st11}
  
  \item \textit{Tuned into Earth}. CNRS International Magazine, \textbf{21}, April 2011
  
  \item \textit{Quelle est la diff\'erence entre un tsunami et un raz-de-mar\'ee?}, Slate.fr, 24 mars 2011 \\ \url{http://www.slate.fr/story/36093/difference-tsunami-raz-de-maree}
  
  \item \textit{Les maths \`a l'\'ecoute de la Terre}. Le Journal du CNRS, \No 245, juin 2010
  
  \item \textit{Simuler une avalanche}. \href{http://www.larecherche.fr/}{La Recherche} N428 -- Avril 2009
  
  \item \textit{Springy sediments may amplify tsunamis}. Issue 2662 of \href{http://www.newscientist.com/}{New Scientist magazine}, 25 June 2008, page 20
  
  \item \textit{Comment na\^it un tsunami?}, Le Mensuel de l'Universit\'e, \No 23, F\'evrier 2008
  
\end{etaremune}